---
title: "Assessing predictive performance of models in the COVID-19 Forcast Hub"
author: "Estee Y Cramer, Nicholas G Reich, "
date: "`r Sys.Date()`"
output:
  rmdformats::html_clean:
    highlight: kate
    number_sections: no
    fig_width: 18
    fig_height: 10
---

#Prelims
```{r setup, include=FALSE}
# hub_root_dir<- "~/Desktop/Reich Lab/eycramer/covid19-forecast-hub" ## ESTEE
hub_root_dir <- "../../covid19-forecast-hub" ## NICK
knitr::opts_chunk$set(message = FALSE, warning = FALSE, echo = FALSE)
source(file.path(hub_root_dir,"/code/processing-fxns/get_next_saturday.R"))
library(zoltr)  ##devtools::install_github("reichlab/zoltr")
library(lme4)
library(lubridate)
library(forecast)
library(kableExtra)
library(tidyverse)
theme_set(theme_bw())
```

```{r read in other files to be used later}
## locations file
locs <- read_csv(file.path(hub_root_dir,"data-locations/locations.csv"))

## dates with issues file
dates_with_issues <- read_csv(file.path(hub_root_dir,"data-truth/Dates_edit_evaluation.csv"))

## stan model files
stan_model_ae <- readRDS("../paper-inputs/20200927-stan-fit-scores-negbin.rds")

## read score files
cum_scores <- read_csv("../paper-inputs/20200929-cum-scores.csv") %>%
  mutate(wis = (.01*interval_2+.025*interval_5+.05*interval_10+.1*interval_20+.15*interval_30+.2*interval_40+.25*interval_50+
                  .3*interval_60+.35*interval_70+.40*interval_80+.45*interval_90+.5*interval_100)/12)  %>% 
  ## select(-starts_with("interval")) %>%
  mutate(first_fcast_sat = get_next_saturday(timezero) + ifelse(wday(timezero)<=2,0,7)) %>%
  mutate(model_code = recode(factor(model),  "CovidAnalytics-DELPHI" = "Purple",  "COVIDhub-ensemble" = "Aqua", 
    "COVIDhub-baseline" = "COVIDhub-baseline","CU-select" = "Green", "LANL-GrowthRate" = "Gray",  
    "MOBS-GLEAM_COVID" = "Red", "UCLA-SuEIR" = "Gold", "YYG-ParamSearch" ="Pink",
    "JHU_IDD-CovidSP" = "Goldenrod", "UMass-MechBayes" = "Maroon",  "UT-Mobility" = "Indigo", "IHME-CurveFit" = "Orange",
    "IowaStateLW-STEM" = "Teal", "PSI-DRAFT" = "Emerald",  "USC-SI_kJalpha" = "Lilac", 
    "USACE-ERDC_SEIR" = "Tan", "GT-DeepCOVID" = "Scarlet", "UA-EpiCovDA" = "Ruby")) %>%
  left_join(locs, by=c("unit" = "location"))

```



```{r not in function,  include=FALSE}
'%!in%' <- function(x,y)!('%in%'(x,y))
```

```{r, echo = FALSE}
## Tuesday the first timezero for which we will be evaluating forecasts
## 1 wk ahead forecasts are for the following Saturday
incl_start_date <- as.Date("2020-04-28")
## Monday the last timezero for the first week in which we will evaluate
incl_end_date <- incl_start_date + 6
## Target end date of the first set of forecasts
wk_ahead_forecast_date <- incl_start_date + 11

## Paste of forecast week
forecast_date_epiweek <- paste0("EW", MMWRweek::MMWRweek(wk_ahead_forecast_date)$MMWRweek)

#max_sat <- as.Date(Upcoming_sat - 21)  #Latest week evaluated
min_sat <- as.Date(get_next_saturday("2020-05-05")) #Earliest week evaluated

#cutoff date for final paper: 2020-08-08
max_sat <- as.Date("2020-08-08")

number_weeks <- as.integer(difftime(max_sat, min_sat, units = "weeks") + 1) #Number of weeks evaluated
```

```{r}
# read in csv with dates to filter out due to errors in reporting
dates_to_filter <- dates_with_issues %>%
  mutate(target_date_sat = lubridate::ymd(date_of_error)) 
## TODO: target_data_sat is not necessarily a saturday?

#scored locations
fips <- locs %>%
    mutate(for_scoring = abbreviation %in% c("US", datasets::state.abb))

# keep only locations that get scored 
fips_scoring <- fips %>% filter(for_scoring)  %>%
  select(-for_scoring)
```



```{r}
unique_cum <- cum_tmp %>%
  group_by(model, target, unit, first_fcast_sat) %>%     
  arrange(timezero) %>%    #include arrange so last timezero is selected 
  mutate(forecast_in_wk = row_number(), 
         last_forecast_in_wk = forecast_in_wk == max(forecast_in_wk)) %>%    #number weekly submission
  filter(last_forecast_in_wk) %>%   #keep latest weekly submission
  mutate(target_date_sat = case_when(target == "1 wk ahead cum death" ~ first_fcast_sat,
                                     target == "2 wk ahead cum death" ~ first_fcast_sat + 7,
                                     target == "3 wk ahead cum death" ~ first_fcast_sat + 14, 
                                     target == "4 wk ahead cum death" ~ first_fcast_sat + 21)) %>% 
  ungroup()
```


#Fix IHME
```{r}
unique_cum_IHMEadjust <- unique_cum  %>%
  filter(model == "IHME-CurveFit") %>% 
  filter(first_fcast_sat == as.Date("2020-05-23") | first_fcast_sat == as.Date("2020-07-11")) %>% 
  filter(target %in% c("2 wk ahead cum death", "3 wk ahead cum death", "4 wk ahead cum death", "5 wk ahead cum death")) %>%
  mutate(target = case_when(target == "2 wk ahead cum death" ~ "1 wk ahead cum death",
                            target == "3 wk ahead cum death" ~ "2 wk ahead cum death",
                            target == "4 wk ahead cum death" ~ "3 wk ahead cum death",
                            target == "5 wk ahead cum death" ~ "4 wk ahead cum death"),
         first_fcast_sat = first_fcast_sat + 7)
```

```{r}
unique_cum <- rbind(unique_cum, unique_cum_IHMEadjust)
```

```{r code for calc and pred DF}
## Keep only unique forecasts for each week

#Keep only 4 target weeks
unique_cum_4targets <- unique_cum %>%
    filter(target %in% c("1 wk ahead cum death", "2 wk ahead cum death", "3 wk ahead cum death", "4 wk ahead cum death")) 

#Count Locations
locations_4targets <- unique_cum_4targets %>% 
  group_by(model_code, target, first_fcast_sat) %>%
  summarise(n_location = n()) %>% 
  ungroup() 

#Count Horizons
horizons_4targets <- unique_cum_4targets %>%
  group_by(model_code, location_name, first_fcast_sat) %>%
  summarize(n_horizons = n())

#Count Submission Weeks with 4 targets 
weeks_4targets_horizon <- unique_cum_4targets %>%
  left_join(horizons_4targets) %>%
  filter(n_horizons == 4) %>%
  group_by(model_code, location_name, target) %>%
  summarise(n_weeks_all_horizon = n())

#Count Submission weeks with 51 locations
weeks_4targets_location <- unique_cum_4targets %>%
  left_join(locations_4targets) %>%
  filter(n_location == 51) %>%
  group_by(model_code, location_name, target) %>%
  summarise(n_weeks_all_loc = n())

cum_tmp %>%
  filter(model_code == "Orange") %>%
  group_by(first_fcast_sat) %>%
  summarise(n = n())
```

```{r}
empirical_df <- unique_cum_4targets %>%
  left_join(locations_4targets) %>%
  left_join(horizons_4targets) %>%
  left_join(weeks_4targets_horizon) %>%
  left_join(weeks_4targets_location) #%>%
## below lines not needed, this is done above
  # mutate(target_date_sat = case_when(target == "1 wk ahead cum death" ~ first_fcast_sat,
  #                                    target == "2 wk ahead cum death" ~ first_fcast_sat + 7,
  #                                    target == "3 wk ahead cum death" ~ first_fcast_sat + 14, 
  #                                    target == "4 wk ahead cum death" ~ first_fcast_sat + 21)) 
```


#Models with all qualifying criteria for cumulative deaths 
```{r}
scored_models_df_calc <- empirical_df %>%
  filter(n_weeks_all_horizon == 14) %>%
  filter(n_weeks_all_loc == 14) %>%
  anti_join(dates_to_filter) %>%  ungroup() 
```


#Models with enough qualifying forecasts for mixed effects model
```{r}
scored_models_df_pred <- empirical_df %>%
  filter(n_location >= 25) %>%
  filter(n_weeks_all_horizon >= 11) %>%
  anti_join(dates_to_filter) %>%  ungroup()  
```

#Mixed Effects model creation

###Models to predict MAE
```{r baseline as ref}
#absolute error model
scored_models_df_pred$model_code <- relevel(scored_models_df_pred$model_code, ref = "COVIDhub-baseline")
```


```{r LMER for AE model-target FE interaction and location and week REs}
cum_fit_abs_errorM1 <- lmer(log(abs_error+0.01) ~ model_code*target + (1|first_fcast_sat) + (1|location_name), data = scored_models_df_pred)
#summary(cum_fit_abs_errorM2)
```

```{r LMER for AE model-target FE interaction and week-location RE interaction}
cum_fit_abs_errorM2 <- lmer(log(abs_error+0.01) ~ model_code*target + (1|first_fcast_sat:location_name), data = scored_models_df_pred)
#summary(cum_fit_abs_errorM2)
```

```{r LMER for AE model-target FE interaction and week*location + week*model RE interactions}
cum_fit_abs_errorM3 <- lmer(log(abs_error+0.01) ~  model_code*target + (1|first_fcast_sat:location_name) + (1|first_fcast_sat:model_code), data = scored_models_df_pred)
#summary(cum_fit_abs_errorM3)
```

```{r LMER for AE model-target FE interaction and week*model*location RE interaction}
cum_fit_abs_errorM4 <- lmer(log(abs_error+0.01) ~  model_code*target + (1|first_fcast_sat:model_code:location_name), data = scored_models_df_pred)
#summary(cum_fit_abs_errorM1)
```

```{r stan model sandbox}

cum_fit_abs_errorM5 <- glmer.nb(round(abs_error) ~  model_code*target + (1|first_fcast_sat:location_name) + (1|first_fcast_sat:model_code), data = scored_models_df_pred)

library(rstanarm)
stan_fit <- stan_glmer(round(abs_error) ~  model_code*target + (1|first_fcast_sat:location_name), 
  chains=1,
  family=neg_binomial_2(),
  data = scored_models_df_pred)
  #data = scored_models_df_pred[sample(nrow(scored_models_df_pred), 1000),])
#summary(cum_fit_abs_errorM1)
```

### Models to predict WIS 
```{r LMER for WIS model-target interaction}
cum_fit_wisM1 <- lmer(log(wis + .01) ~  model_code*target + (1|first_fcast_sat:model_code:location_name), data = scored_models_df_pred)
#summary(cum_fit_wisM1)
```

```{r LMER for WIS model-target and model-location interaction}
cum_fit_wisM2 <- lmer(log(wis + .01) ~ model_code*target + (1|first_fcast_sat:location_name), data = scored_models_df_pred)

#summary(cum_fit_wisM2)
```

```{r LMER for WIS model-target and model-week interaction}
cum_fit_wisM3 <- lmer(log(wis + .01) ~ model_code*target +  (1|first_fcast_sat:location_name) + (1|first_fcast_sat:model_code), data = scored_models_df_pred)

#summary(cum_fit_wisM3)
```

Dataframe for model fitting
```{r Create DF for MAE and WIS predictions}
model_count_cum <- nrow(unique(scored_models_df_pred %>% group_by(model_code) %>% filter(model_code != "Tan" | model_code != "Orange") %>% summarise(n = n())))

#To create a dataframe of predictions based on the model, I've create a dataframe that includes the names of all teams as well as the targets, locations, and submission weeks. This is an emplty datafram that gets filled in using the predict function. 

total_forecast_count <- number_weeks * 4 * 51          #Count number of forecasts for each team
total_location_count <- number_weeks * 4               #Total number of locations submitted for each team

first_fcast_sat_unique <- unique(scored_models_df_pred$first_fcast_sat)
weeks_repeat4times <- first_fcast_sat_unique %>% magrittr::extract(. <= as.Date(max_sat)) 

target_unique <- unique(scored_models_df_pred$target)

model_code <- c("Ruby", "Teal", "Goldenrod", "Emerald", "Scarlet", "Purple", "COVIDhub-baseline", "Aqua", "Green", "Red", "Gold", "Maroon", "Indigo", "Pink")

#Create DF for MAE and WIS predictions (step 2) 
model_code <- rep(model_code, each = total_forecast_count)   #repeat model names number of times of forecast 
location_name <- rep(rep(fips_scoring$location_name, each = total_location_count), 14) #Repeat locations 

#Repeat number of first forecast dates 
first_fcast_sat <- rep(rep(weeks_repeat4times, each = 4), 714)

#Repat number of targets taking into account weeks with 3 - 1 targets 
target <-  rep(target_unique, 9996)

length(model_code)
length(location_name)
length(first_fcast_sat)
length(target)

prediction_df = data.frame(model_code, location_name, first_fcast_sat, target) #merge all vectors into a dataframe
```

```{r}
#predict MAE
log_abs_errorM1 <- predict(cum_fit_abs_errorM1, prediction_df, allow.new.levels = TRUE)    #predict abs error based on mixed effects model
prediction_df$abs_errorM1 <- exp(log_abs_errorM1) - .01           #exponentiate log

log_abs_errorM2 <- predict(cum_fit_abs_errorM2, prediction_df)    
prediction_df$abs_errorM2 <- exp(log_abs_errorM2) - .01           

log_abs_errorM3 <- predict(cum_fit_abs_errorM3, prediction_df, allow.new.levels = TRUE)    
prediction_df$abs_errorM3 <- exp(log_abs_errorM3) - .01        

#Predict WIS
log_wisM1 <- predict(cum_fit_wisM1, prediction_df,allow.new.levels = TRUE)
prediction_df$wisM1 <- exp(log_wisM1) - .01

log_wisM2 <- predict(cum_fit_wisM2, prediction_df, allow.new.levels = TRUE)
prediction_df$wisM2 <- exp(log_wisM2) - .01

log_wisM3 <- predict(cum_fit_wisM3, prediction_df, allow.new.levels = TRUE)
prediction_df$wisM3 <- exp(log_wisM3) - .01
```

```{r}
predict_df_MAE <- prediction_df %>%
  pivot_longer(cols = starts_with("abs_error"), values_to = "MAE_value", names_to = "mae_modelnum") %>%
  mutate(mae_modelnum = as.factor(mae_modelnum))


predict_df_WIS <- prediction_df %>%
  pivot_longer(cols = starts_with("wisM"), values_to = "wis_value", names_to = "wis_modelnum") %>%
mutate(wis_modelnum = as.factor(wis_modelnum))
```


# Table 2: prediction interval empirical coverage for cumulative deaths by horizon 
```{r}
#only query specific models and timezeros that are needed. Require table to say which are needed for each model. Use unique_cum to specify which timezeros are needed for eval. (maybe)
calculated_models1 <- c("UCLA-SuEIR", "CU-select", "LANL-GrowthRate", "MOBS-GLEAM_COVID")
calculated_models2<- c( "COVIDhub-ensemble", "CovidAnalytics-DELPHI", "YYG-ParamSearch", "COVIDhub-baseline")

cum_calibration <- do_zoltar_query(zoltar_connection, 
                                   project_url =  "https://zoltardata.com/api/project/44/",
                                   is_forecast_query = TRUE,
                                   models = calculated_models1, 
                                   units = the_locations, 
                                   targets = the_targets_cum,
                                   timezeros = the_timezeros_cum, 
                                   scores = the_intervals, 
                                   types = c("quantile")) %>%
  filter(quantile == .025 | quantile == .25 | quantile == .75 | quantile == .975) %>%
  filter(timezero <= as.Date("2020-08-08"))

cum_calibration2 <- do_zoltar_query(zoltar_connection, 
                                   project_url =  "https://zoltardata.com/api/project/44/",
                                   is_forecast_query = TRUE,
                                   models = calculated_models2, 
                                   units = the_locations, 
                                   targets = the_targets_cum,
                                   timezeros = the_timezeros_cum, 
                                   scores = the_intervals, 
                                   types = c("quantile")) %>%
  filter(quantile == .025 | quantile == .25 | quantile == .75 | quantile == .975) %>%
  filter(timezero <= as.Date("2020-08-08"))

cum_calibration <- rbind(cum_calibration, cum_calibration2)
```


```{r}
cum_truth <- unique_cum  %>% 
  filter(model_code %in% c("Purple", "COVIDhub-baseline", "Aqua", "Green",  "Gray", "Red", "Gold", "Pink", "Orange")) %>%
  select(model_code, model, timezero, unit, target, truth, first_fcast_sat) %>% anti_join(dates_to_filter)
```

```{r}
cum_calibration_wide <- cum_calibration %>%
  select(model, timezero, unit, target, value, quantile) %>%
  pivot_wider(names_from = quantile, values_from = value) %>% 
  right_join(cum_truth) %>% ungroup()

colnames(cum_calibration_wide) <- c("model", "timezero", "unit", "target", "interval_025", "interval_25",  "interval_75","interval_975", "model_code", "truth", "first_fcast_sat")

calibration_scores <- cum_calibration_wide %>%
  mutate(calib_95 = ifelse(truth >= interval_025 & truth <= interval_975, 1, 0)) %>%
  mutate(calib_50 = ifelse(truth >= interval_25 & truth <= interval_75, 1, 0)) %>%
  group_by(model, target) %>%
  summarise(percent_calib50 = round(sum(calib_50)/ n(),3),
            percent_calib95 = round(sum(calib_95) / n(),3))

calibration_table <- calibration_scores %>%
  pivot_wider(names_from = target, values_from = c(percent_calib50, percent_calib95)) %>%
  select("model", "percent_calib50_1 wk ahead cum death", 
       "percent_calib50_2 wk ahead cum death",  "percent_calib50_3 wk ahead cum death", "percent_calib50_4 wk ahead cum death",  "percent_calib50_5 wk ahead cum death", 
       "percent_calib50_6 wk ahead cum death", "percent_calib50_7 wk ahead cum death",   "percent_calib50_8 wk ahead cum death",  "percent_calib50_9 wk ahead cum death", 
       "percent_calib50_10 wk ahead cum death", "percent_calib50_11 wk ahead cum death",  "percent_calib50_12 wk ahead cum death", "percent_calib50_13 wk ahead cum death", "percent_calib50_14 wk ahead cum death","percent_calib95_1 wk ahead cum death", "percent_calib95_2 wk ahead cum death", "percent_calib95_3 wk ahead cum death", "percent_calib95_4 wk ahead cum death","percent_calib95_5 wk ahead cum death", "percent_calib95_6 wk ahead cum death",  "percent_calib95_7 wk ahead cum death", "percent_calib95_8 wk ahead cum death",  "percent_calib95_9 wk ahead cum death", "percent_calib95_10 wk ahead cum death",  "percent_calib95_11 wk ahead cum death",  "percent_calib95_12 wk ahead cum death","percent_calib95_13 wk ahead cum death", "percent_calib95_14 wk ahead cum death")
```


#Figure 1: Schematic of a forecast: timeline, targets, quantiles, etc…







#Figure 2: overall average performance of each model, by target. 
```{r dataframes for targets}
##Average score across all locations calculated MAE and WIS
average_byweek_calc <- scored_models_df_calc %>%  #scored_models_df_pred includes forecasts from models that have been selected for scoring
  group_by(model_code, target) %>%
  summarise(MAE  = round(mean(abs_error, na.rm = T),1),  #calc MAE
            mae_rank = rank(MAE),                       #rank(MAE). (previously used for color scheme but no longer used)
        n_obs_ae=sum(!is.na(abs_error)),
         avg_wis = round(mean(wis, na.rm = T),1),       #calc wis
        n_obs_int=sum(!is.na(wis))) %>%                 #sanity check count
  ungroup() %>%
  group_by(target) %>%                                   
  mutate(mae_rank = rank(MAE,ties.method = "min")) %>%
  mutate(wis_rank = rank(avg_wis)) %>% 
  mutate_at(vars(matches("MAE")), funs(diff_baseline = (((.- .[model_code=="COVIDhub-baseline"]) / .[model_code=="COVIDhub-baseline"])*100))) %>%
 mutate_at(vars(matches("avg_wis")), funs(diff_baseline = (((.- .[model_code=="COVIDhub-baseline"]) / .[model_code=="COVIDhub-baseline"])*100))) %>%
  ungroup() 

##Average score across all locations based on predicted MAE 
average_byweek_pred_MAE <- predict_df_MAE %>%  #scored_models_df_pred includes forecasts from models that have been selected for scoring
  group_by(model_code, target, mae_modelnum) %>%
  summarise(MAE  = round(mean(MAE_value, na.rm = T),1),  #calc MAE
        n_obs_ae=sum(!is.na(MAE_value))) %>%
  ungroup() %>%
  group_by(mae_modelnum, target) %>%                                   
  mutate_at(vars(ends_with("MAE")), funs(MAE_diff_baseline = (((.- .[model_code=="COVIDhub-baseline"]) / .[model_code=="COVIDhub-baseline"])*100))) %>% ungroup()

#Predicted WIS
average_byweek_pred_wis <- predict_df_WIS  %>%  #scored_models_df_pred includes forecasts from models that have been selected for scoring
  group_by(model_code, target, wis_modelnum) %>%
  summarise(wis  = round(mean(wis_value, na.rm = T),1),  #calc MAE
        n_obs_ae=sum(!is.na(wis_value))) %>%
  ungroup() %>%
  group_by(wis_modelnum, target) %>%                                   
  mutate_at(vars(ends_with("wis")), funs(wis_diff_baseline = (((.- .[model_code=="COVIDhub-baseline"]) / .[model_code=="COVIDhub-baseline"])*100))) %>% ungroup()
```

```{r Panel 1A: Calculated MAE}
average_byweek_calc$model_code <- reorder(average_byweek_calc$model_code, average_byweek_calc$MAE)

Strat_target_MAE_calc <- ggplot(average_byweek_calc, aes(x=model_code, y=target, fill= MAE_diff_baseline)) + 
  geom_tile() +
  geom_text(aes(label=round(MAE)), size = 6) +
  scale_fill_gradient2(low = "blue2",
  high = "red", midpoint = 0,  name = "% change from baseline") + 
  xlab("Scored Models") + ylab("Forecast Target") +
  theme(axis.text.x =  element_text(angle = 45, hjust = 1, size = 16),
        axis.title.x=element_blank(),
        axis.text.y = element_text(size = 16)) +
  guides(fill = FALSE) + 
  ggtitle("Calculated MAE")
```

```{r Panel 1B-D: Pred MAE}
average_byweek_pred_MAE$model_code <- reorder(average_byweek_pred_MAE$model_code, average_byweek_pred_MAE$MAE)

Strat_target_MAE_pred <- ggplot(average_byweek_pred_MAE, aes(x=model_code, y=target, fill= round(MAE_diff_baseline,2))) + 
  geom_tile() +
  geom_text(aes(label=round(MAE)), size = 6) +
  scale_fill_gradient2(low = "blue2",
  high = "red", midpoint = 0,  name = "% change from baseline") + 
  xlab("Scored Models") + ylab("Forecast Target") +
  theme(axis.text.x =  element_text(angle = 45, hjust = 1, size = 16), 
        axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.title.x=element_blank()) + 
  facet_wrap( ~ mae_modelnum, ncol = 1) +
  guides(fill = FALSE) + 
  ggtitle("Predicted MAE")
```

```{r Panel 2A: Calc WIS}
average_byweek_calc$model_code <- reorder(average_byweek_calc$model_code, average_byweek_calc$avg_wis)

Strat_target_WIS_calc <- ggplot(average_byweek_calc, aes(x=model_code, y=target, fill= diff_baseline)) + 
  geom_tile() +
  geom_text(aes(label=round(avg_wis,0)), size = 6) +
  scale_fill_gradient2(low = "blue", high = "red", midpoint = 0, name = "% Change from baseline")+ 
  xlab("Scored model_codes") + 
  theme(axis.text.x =  element_text(angle = 45, hjust = 1, size = 16),
        axis.title.x=element_blank(),
        axis.text.y = element_text(size = 16)) +
  ggtitle("Calculated WIS")
```

```{r Panel 2B-D: pred WIS}
average_byweek_pred_wis$model_code <- reorder(average_byweek_pred_wis$model_code, average_byweek_pred_wis$wis)

Strat_target_wis_pred <- ggplot(average_byweek_pred_wis, aes(x=model_code, y=target, fill= round(wis_diff_baseline,2))) + 
  geom_tile() +
  geom_text(aes(label=round(wis)), size = 6) +
  scale_fill_gradient2(low = "blue2",
  high = "red", midpoint = 0,  name = "% change from baseline") + 
  xlab("Scored Models") + ylab("Forecast Target") +
  theme(axis.text.x =  element_text(angle = 45, hjust = 1, size = 16), 
        axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.title.x=element_blank()) + 
  facet_wrap( ~ wis_modelnum, ncol = 1) +
  ggtitle("Predicted WIS")
```

```{r, fig.width= 15, fig.height= 20}
gridExtra::grid.arrange(Strat_target_MAE_calc, Strat_target_WIS_calc,  Strat_target_MAE_pred, Strat_target_wis_pred)
```


#Figure 3: average performance of each model by location (emperical estimates)
```{r df for figure 3 }
location_fig3 <- empirical_df %>%
  filter(n_weeks_all_horizon == 14) %>%
  filter(n_location >= 25) %>%
  anti_join(dates_to_filter) %>%  ungroup() 

average_by_loc_calc <- location_fig3 %>%
  group_by(model_code, location_name) %>% 
  summarise(MAE  = round(mean(abs_error),1),        #calc MAE
        n_obs_ae = sum(abs_error),          #sanity check (not used in graph)
        avg_wis = round(mean(wis),1),    #calc WIS       
        n_obs_int=sum(wis)) %>% 
  group_by(location_name) %>%     
mutate_at(vars(matches("MAE")), funs(diff_baseline_MAE = (((.- .[model_code=="COVIDhub-baseline"]) / .[model_code=="COVIDhub-baseline"])*100))) %>%   #calculate MAE % change from baseline
mutate_at(vars(matches("avg_wis")), funs(diff_baseline_wis = (((.- .[model_code=="COVIDhub-baseline"]) / .[model_code=="COVIDhub-baseline"])*100))) %>% 
mutate_at(vars(matches("MAE")), funs(relative_basemae = (. / .[model_code=="COVIDhub-baseline"]))) %>%
mutate_at(vars(matches("avg_wis")), funs(relative_basewis = (./ .[model_code=="COVIDhub-baseline"]))) %>%
  ungroup()
```

```{r plot figure 3a MAE, fig.width=18, fig.height=10}
average_by_loc_calc$model_code <- reorder(average_by_loc_calc$model_code, average_by_loc_calc$MAE) #sort models by MAE for plot
average_by_loc_calc$location_name <- reorder(average_by_loc_calc$location_name, average_by_loc_calc$MAE)

ggplot(average_by_loc_calc, aes(x=model_code, y=location_name, fill= diff_baseline_MAE)) +
  geom_tile() +
  geom_text(aes(label=round(MAE))) +
  scale_fill_gradient2(low = "navy", high = "red", name = "% Change from baseline")+ 
  xlab("Scored Models") + ylab("Location") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

```{r plot figure 3b WIS, fig.width=18, fig.height=10}

average_by_loc_calc$model_code <- reorder(average_by_loc_calc$model_code, average_by_loc_calc$avg_wis) #sort models by MAE for plot
average_by_loc_calc$location_name <- reorder(average_by_loc_calc$location_name, average_by_loc_calc$avg_wis)


ggplot(average_by_loc_calc, aes(x=model_code, y=location_name, fill= diff_baseline_wis)) +
  geom_tile() +
  geom_text(aes(label=round(avg_wis))) +
  scale_fill_gradient2(low = "navy", high = "red", name = "% Change from baseline")+ 
  xlab("Scored Models") + ylab("Location") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```



#Figure 4: average performance of each model by week (averaged across locations, not imputed for weeks that are missing)

```{r}
myColors_cum <- c("black", "cyan2", "firebrick3",
                  "goldenrod4", "darkgreen", "brown2", 
                  "blue4", "darkorchid", "cadetblue2", 
                  "seagreen3", "red",  "darkgoldenrod1", 
                  "brown", "deeppink1", "darkorange")

names(myColors_cum) <- c("COVIDhub-baseline", "Teal", "Ruby",
                         "Goldenrod", "Emerald", "Scarlet", 
                         "Indigo", "Purple", "Aqua",
                         "Green",  "Red",  "Gold",  
                         "Maroon", "Pink", "Orange")

colScale_cum <- scale_colour_manual(name = "model_code", values = myColors_cum)
```

```{r}
average_byweek_calc <- empirical_df %>%
  filter(n_location == 51) %>%
  filter(n_horizons == 4) %>%
  group_by(model_code, first_fcast_sat) %>%
  summarise(mae = round(mean(abs_error, na.rm = T), 1),
        n_obs_ae = sum(!is.na(abs_error)), 
        avg_wis = round(mean(wis, na.rm=TRUE),1), 
        n_obs_int=sum(!is.na(wis))) %>% 
   group_by(first_fcast_sat) %>%
  mutate_at(vars(ends_with("MAE")), funs(relative_basewis = ((. - .[model_code=="COVIDhub-baseline"]) / .[model_code=="COVIDhub-baseline"])*100)) %>%
  mutate_at(vars(ends_with("avg_wis")), funs(relative_basemae = ((. - .[model_code=="COVIDhub-baseline"]) / .[model_code=="COVIDhub-baseline"])*100)) %>%
  ungroup() %>% arrange(first_fcast_sat, model_code)
```


```{r Figure 4 Panel 1A}
#Plot of MAE stratified by submission week
week_MAE <- ggplot(average_byweek_calc, aes(x= lubridate::ymd(first_fcast_sat), y=mae, color = model_code, fill = model_code)) +
  scale_x_date(date_labels = "%Y-%m-%d", breaks = c(first_fcast_sat)) + 
  geom_line() + 
  colScale_cum +
  geom_point(size = 2) + 
  xlab("1 Week Ahead Target Date") + ylab(NULL) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 15)) +
  ggtitle("MAE")
```


```{r Figure 4 Panel 2A}
week_mae_relative <- ggplot(average_byweek_calc, aes(x= lubridate::ymd(first_fcast_sat), y=relative_basemae, color = model_code, fill = model_code)) +
  scale_x_date(date_labels = "%Y-%m-%d", breaks = c(first_fcast_sat)) +
  #scale_color_manual(values = colors2) +
   geom_line() + 
  colScale_cum +
  geom_point(size = 2, value = colors) + 
  xlab("1 week ahead target date") + ylab(NULL) + ggtitle("MAE relative to baseline") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 15))
```

```{r Panel 1B}
#Plot of MAE stratified by submission week
week_wis <- ggplot(average_byweek_calc, aes(x= lubridate::ymd(first_fcast_sat), y=avg_wis, color = model_code, fill = model_code)) +
  scale_x_date(date_labels = "%Y-%m-%d", breaks = c(first_fcast_sat)) + 
  geom_line() + 
  colScale_cum +
  geom_point(size = 2) + 
  xlab("1 Week Ahead Target Date") + ylab(NULL) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 15)) +
  ggtitle("WIS")
```

```{r Figure 4 Panel 2B}
week_wis_relative <- ggplot(average_byweek_calc, aes(x= lubridate::ymd(first_fcast_sat), y=relative_basewis, color = model_code, fill = model_code)) +
  scale_x_date(date_labels = "%Y-%m-%d", breaks = c(first_fcast_sat)) +
  #scale_color_manual(values = colors2) +
   geom_line() + 
  colScale_cum +
  geom_point(size = 2, value = colors) + 
 # xlab("1 week ahead target date") + ylab(NULL) + ggtitle("WIS relative to baseline") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 15))
```

```{r, fig.width= 10, fig.height= 15}
#gridExtra::grid.arrange(week_MAE, week_mae_relative, week_wis, week_wis_relative)
```


```{r}
#Incidence dataset
# inc_tmp <- do_zoltar_query(zoltar_connection, 
#                            project_url =  "https://zoltardata.com/api/project/44/",
#                            is_forecast_query = FALSE,
#                            models = the_models,
#                            units = the_locations,
#                            targets = the_targets_inc,
#                            timezeros = the_timezeros_inc, 
#                            scores = the_scores) %>%
#    left_join(fips, by=c("unit" = "location")) %>%
#   mutate(wis = (.01*interval_2+.025*interval_5+.05*interval_10+.1*interval_20+.15*interval_30+.2*interval_40+.25*interval_50+
#                   .3*interval_60+.35*interval_70+.40*interval_80+.45*interval_90+.5*interval_100)/12, na.rm = TRUE)  %>%
#   mutate(first_fcast_sat = get_next_saturday(timezero) + ifelse(wday(timezero)<=2,0,7))
```




