---
title: "Assessing predictive performance of models in the COVID-19 Forcast Hub"
author: "Estee Y Cramer, Nicholas G Reich, "
date: "`r Sys.Date()`"
output:
  rmdformats::html_clean:
    highlight: kate
    number_sections: no
    fig_width: 18
    fig_height: 10
---

#Prelims
```{r global parameters}
## set hub directory on local machine
# hub_root_dir<- "~/Desktop/Reich Lab/eycramer/covid19-forecast-hub" ## ESTEE
hub_root_dir <- "../covid19-forecast-hub" ## NICK

## minimum number of weeks for eligibility
NUM_WEEKS_CUM <- 11
NUM_WEEKS_INC <- 8

## minumum number of models in a week to be considered eligible
NUM_MODELS <- 25

```


```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE, echo = FALSE)
source(file.path(hub_root_dir,"/code/processing-fxns/get_next_saturday.R"))
library(lubridate)
library(kableExtra)
library(tidyverse)
theme_set(theme_bw())
```

```{r read in other files to be used later}
## locations file
locs <- read_csv(file.path(hub_root_dir,"data-locations/locations.csv"))

## locations/dates with reporting anomalies
dates_with_issues <- read_csv("paper-inputs/anomaly-reporting-dates.csv") %>%
  filter(to_remove==1)

## stan model files
stan_model_ae <- readRDS("paper-inputs/20200927-stan-fit-scores-negbin.rds")

## read model eligibility file
model_eligibility <- read_csv("paper-inputs/model-eligibility.csv")

## read score files
cum_scores <- read_csv("paper-inputs/20200929-cum-scores.csv") 
```


```{r remove scores from ineligible models}
## find models with minimum eligibility for full analysis
cum_eligible_models <- model_eligibility %>%
  group_by(model) %>%
  summarize(num_eligible_weeks = sum(!is.na(timezero) & num_units_eligible_cum >= NUM_MODELS)) %>%
  filter(num_eligible_weeks > NUM_WEEKS_CUM) %>%
  pull(model)

inc_eligible_models <- model_eligibility %>%
  group_by(model) %>%
  summarize(num_eligible_weeks = sum(!is.na(timezero) & num_units_eligible_cum >= NUM_MODELS)) %>%
  filter(num_eligible_weeks > NUM_WEEKS_INC) %>%
  pull(model)

## filter scores
cum_scores_eligible <- cum_scores %>%
  filter(model %in% cum_eligible_models) 

# inc_scores_eligible <- inc_scores %>%
#   filter(model %in% inc_eligible_models)
```


```{r remove scores from location-weeks with contaminated data}
cum_scores_eligible$to_keep <- TRUE
for(j in 1:nrow(dates_with_issues)){
  tmp.idx <- which(cum_scores_eligible$timezero <= dates_with_issues$first_fcast_date_impacted[j] & cum_scores_eligible$unit == dates_with_issues$fips[j])
  cum_scores_eligible$to_keep[tmp.idx] <- FALSE
}

# inc_scores_eligible$to_keep <- TRUE
# for(j in 1:nrow(dates_with_issues)){
#   tmp.idx <- which(inc_scores_eligible$timezero <= dates_with_issues$first_fcast_date_impacted[j] & inc_scores_eligible$unit == dates_with_issues$fips[j])
#   inc_scores_eligible$to_keep[tmp.idx] <- FALSE
# }

cum_scores_eligible <- cum_scores_eligible %>% 
  filter(to_keep) %>%
  select(-to_keep)

# inc_scores_eligible <- inc_scores_eligible %>% 
#   filter(to_keep) %>%
#   select(-to_keep)

```



```{r add blinded model code}
possible_colors <- c("Purple", "Aqua", "Green", "Gray", "Red", "Gold", "Pink", 
  "Goldenrod", "Maroon", "Indigo", "Orange", "Teal", "Emerald", "Lilac", 
  "Tan", "Scarlet", "Ruby")

cum_scores_eligible$model_code <- factor(cum_scores_eligible$model, labels=sample(possible_colors, size = length(cum_eligible_models), replace = FALSE))
# inc_scores_eligible$model_code <- factor(inc_scores_eligible$model, labels=sample(possible_colors, size = length(inc_eligible_models), replace = FALSE))
```


```{r prepare scores for analysis}
cum_scores_calc <- cum_scores_eligible %>%
  mutate(wis = (.01*interval_2+.025*interval_5+.05*interval_10+.1*interval_20+.15*interval_30+.2*interval_40+.25*interval_50+
                  .3*interval_60+.35*interval_70+.40*interval_80+.45*interval_90+.5*interval_100)/12)  %>% 
  #select(-starts_with("interval")) %>%
  mutate(first_fcast_sat = get_next_saturday(timezero) + ifelse(wday(timezero)<=2,0,7)) %>%
  left_join(locs, by=c("unit" = "location"))
```


```{r code for calc and pred DF}
## Keep only unique forecasts for each week

#Keep only 4 target weeks
unique_cum_4targets <- unique_cum %>%
    filter(target %in% c("1 wk ahead cum death", "2 wk ahead cum death", "3 wk ahead cum death", "4 wk ahead cum death")) 

#Count Locations
locations_4targets <- unique_cum_4targets %>% 
  group_by(model_code, target, first_fcast_sat) %>%
  summarise(n_location = n()) %>% 
  ungroup() 

#Count Horizons
horizons_4targets <- unique_cum_4targets %>%
  group_by(model_code, location_name, first_fcast_sat) %>%
  summarize(n_horizons = n())

#Count Submission Weeks with 4 targets 
weeks_4targets_horizon <- unique_cum_4targets %>%
  left_join(horizons_4targets) %>%
  filter(n_horizons == 4) %>%
  group_by(model_code, location_name, target) %>%
  summarise(n_weeks_all_horizon = n())

#Count Submission weeks with 51 locations
weeks_4targets_location <- unique_cum_4targets %>%
  left_join(locations_4targets) %>%
  filter(n_location == 51) %>%
  group_by(model_code, location_name, target) %>%
  summarise(n_weeks_all_loc = n())

cum_tmp %>%
  filter(model_code == "Orange") %>%
  group_by(first_fcast_sat) %>%
  summarise(n = n())
```

```{r}
empirical_df <- unique_cum_4targets %>%
  left_join(locations_4targets) %>%
  left_join(horizons_4targets) %>%
  left_join(weeks_4targets_horizon) %>%
  left_join(weeks_4targets_location) #%>%
## below lines not needed, this is done above
  # mutate(target_date_sat = case_when(target == "1 wk ahead cum death" ~ first_fcast_sat,
  #                                    target == "2 wk ahead cum death" ~ first_fcast_sat + 7,
  #                                    target == "3 wk ahead cum death" ~ first_fcast_sat + 14, 
  #                                    target == "4 wk ahead cum death" ~ first_fcast_sat + 21)) 
```


#Models with all qualifying criteria for cumulative deaths 
```{r}
scored_models_df_calc <- empirical_df %>%
  filter(n_weeks_all_horizon == 14) %>%
  filter(n_weeks_all_loc == 14) %>%
  anti_join(dates_to_filter) %>%  ungroup() 
```


#Models with enough qualifying forecasts for mixed effects model
```{r}
scored_models_df_pred <- empirical_df %>%
  filter(n_location >= 25) %>%
  filter(n_weeks_all_horizon >= 11) %>%
  anti_join(dates_to_filter) %>%  ungroup()  
```





# Table 2: prediction interval empirical coverage for cumulative deaths by horizon 
```{r}
#only query specific models and timezeros that are needed. Require table to say which are needed for each model. Use unique_cum to specify which timezeros are needed for eval. (maybe)
calculated_models1 <- c("UCLA-SuEIR", "CU-select", "LANL-GrowthRate", "MOBS-GLEAM_COVID")
calculated_models2<- c( "COVIDhub-ensemble", "CovidAnalytics-DELPHI", "YYG-ParamSearch", "COVIDhub-baseline")

cum_calibration <- do_zoltar_query(zoltar_connection, 
                                   project_url =  "https://zoltardata.com/api/project/44/",
                                   is_forecast_query = TRUE,
                                   models = calculated_models1, 
                                   units = the_locations, 
                                   targets = the_targets_cum,
                                   timezeros = the_timezeros_cum, 
                                   scores = the_intervals, 
                                   types = c("quantile")) %>%
  filter(quantile == .025 | quantile == .25 | quantile == .75 | quantile == .975) %>%
  filter(timezero <= as.Date("2020-08-08"))

cum_calibration2 <- do_zoltar_query(zoltar_connection, 
                                   project_url =  "https://zoltardata.com/api/project/44/",
                                   is_forecast_query = TRUE,
                                   models = calculated_models2, 
                                   units = the_locations, 
                                   targets = the_targets_cum,
                                   timezeros = the_timezeros_cum, 
                                   scores = the_intervals, 
                                   types = c("quantile")) %>%
  filter(quantile == .025 | quantile == .25 | quantile == .75 | quantile == .975) %>%
  filter(timezero <= as.Date("2020-08-08"))

cum_calibration <- rbind(cum_calibration, cum_calibration2)
```


```{r}
cum_truth <- unique_cum  %>% 
  filter(model_code %in% c("Purple", "COVIDhub-baseline", "Aqua", "Green",  "Gray", "Red", "Gold", "Pink", "Orange")) %>%
  select(model_code, model, timezero, unit, target, truth, first_fcast_sat) %>% anti_join(dates_to_filter)
```

```{r}
cum_calibration_wide <- cum_calibration %>%
  select(model, timezero, unit, target, value, quantile) %>%
  pivot_wider(names_from = quantile, values_from = value) %>% 
  right_join(cum_truth) %>% ungroup()

colnames(cum_calibration_wide) <- c("model", "timezero", "unit", "target", "interval_025", "interval_25",  "interval_75","interval_975", "model_code", "truth", "first_fcast_sat")

calibration_scores <- cum_calibration_wide %>%
  mutate(calib_95 = ifelse(truth >= interval_025 & truth <= interval_975, 1, 0)) %>%
  mutate(calib_50 = ifelse(truth >= interval_25 & truth <= interval_75, 1, 0)) %>%
  group_by(model, target) %>%
  summarise(percent_calib50 = round(sum(calib_50)/ n(),3),
            percent_calib95 = round(sum(calib_95) / n(),3))

calibration_table <- calibration_scores %>%
  pivot_wider(names_from = target, values_from = c(percent_calib50, percent_calib95)) %>%
  select("model", "percent_calib50_1 wk ahead cum death", 
       "percent_calib50_2 wk ahead cum death",  "percent_calib50_3 wk ahead cum death", "percent_calib50_4 wk ahead cum death",  "percent_calib50_5 wk ahead cum death", 
       "percent_calib50_6 wk ahead cum death", "percent_calib50_7 wk ahead cum death",   "percent_calib50_8 wk ahead cum death",  "percent_calib50_9 wk ahead cum death", 
       "percent_calib50_10 wk ahead cum death", "percent_calib50_11 wk ahead cum death",  "percent_calib50_12 wk ahead cum death", "percent_calib50_13 wk ahead cum death", "percent_calib50_14 wk ahead cum death","percent_calib95_1 wk ahead cum death", "percent_calib95_2 wk ahead cum death", "percent_calib95_3 wk ahead cum death", "percent_calib95_4 wk ahead cum death","percent_calib95_5 wk ahead cum death", "percent_calib95_6 wk ahead cum death",  "percent_calib95_7 wk ahead cum death", "percent_calib95_8 wk ahead cum death",  "percent_calib95_9 wk ahead cum death", "percent_calib95_10 wk ahead cum death",  "percent_calib95_11 wk ahead cum death",  "percent_calib95_12 wk ahead cum death","percent_calib95_13 wk ahead cum death", "percent_calib95_14 wk ahead cum death")
```


#Figure 1: Schematic of a forecast: timeline, targets, quantiles, etc…







#Figure 2: overall average performance of each model, by target. 
```{r dataframes for targets}
##Average score across all locations calculated MAE and WIS
average_byweek_calc <- scored_models_df_calc %>%  #scored_models_df_pred includes forecasts from models that have been selected for scoring
  group_by(model_code, target) %>%
  summarise(MAE  = round(mean(abs_error, na.rm = T),1),  #calc MAE
            mae_rank = rank(MAE),                       #rank(MAE). (previously used for color scheme but no longer used)
        n_obs_ae=sum(!is.na(abs_error)),
         avg_wis = round(mean(wis, na.rm = T),1),       #calc wis
        n_obs_int=sum(!is.na(wis))) %>%                 #sanity check count
  ungroup() %>%
  group_by(target) %>%                                   
  mutate(mae_rank = rank(MAE,ties.method = "min")) %>%
  mutate(wis_rank = rank(avg_wis)) %>% 
  mutate_at(vars(matches("MAE")), funs(diff_baseline = (((.- .[model_code=="COVIDhub-baseline"]) / .[model_code=="COVIDhub-baseline"])*100))) %>%
 mutate_at(vars(matches("avg_wis")), funs(diff_baseline = (((.- .[model_code=="COVIDhub-baseline"]) / .[model_code=="COVIDhub-baseline"])*100))) %>%
  ungroup() 

##Average score across all locations based on predicted MAE 
average_byweek_pred_MAE <- predict_df_MAE %>%  #scored_models_df_pred includes forecasts from models that have been selected for scoring
  group_by(model_code, target, mae_modelnum) %>%
  summarise(MAE  = round(mean(MAE_value, na.rm = T),1),  #calc MAE
        n_obs_ae=sum(!is.na(MAE_value))) %>%
  ungroup() %>%
  group_by(mae_modelnum, target) %>%                                   
  mutate_at(vars(ends_with("MAE")), funs(MAE_diff_baseline = (((.- .[model_code=="COVIDhub-baseline"]) / .[model_code=="COVIDhub-baseline"])*100))) %>% ungroup()

#Predicted WIS
average_byweek_pred_wis <- predict_df_WIS  %>%  #scored_models_df_pred includes forecasts from models that have been selected for scoring
  group_by(model_code, target, wis_modelnum) %>%
  summarise(wis  = round(mean(wis_value, na.rm = T),1),  #calc MAE
        n_obs_ae=sum(!is.na(wis_value))) %>%
  ungroup() %>%
  group_by(wis_modelnum, target) %>%                                   
  mutate_at(vars(ends_with("wis")), funs(wis_diff_baseline = (((.- .[model_code=="COVIDhub-baseline"]) / .[model_code=="COVIDhub-baseline"])*100))) %>% ungroup()
```

```{r Panel 1A: Calculated MAE}
average_byweek_calc$model_code <- reorder(average_byweek_calc$model_code, average_byweek_calc$MAE)

Strat_target_MAE_calc <- ggplot(average_byweek_calc, aes(x=model_code, y=target, fill= MAE_diff_baseline)) + 
  geom_tile() +
  geom_text(aes(label=round(MAE)), size = 6) +
  scale_fill_gradient2(low = "blue2",
  high = "red", midpoint = 0,  name = "% change from baseline") + 
  xlab("Scored Models") + ylab("Forecast Target") +
  theme(axis.text.x =  element_text(angle = 45, hjust = 1, size = 16),
        axis.title.x=element_blank(),
        axis.text.y = element_text(size = 16)) +
  guides(fill = FALSE) + 
  ggtitle("Calculated MAE")
```

```{r Panel 1B-D: Pred MAE}
average_byweek_pred_MAE$model_code <- reorder(average_byweek_pred_MAE$model_code, average_byweek_pred_MAE$MAE)

Strat_target_MAE_pred <- ggplot(average_byweek_pred_MAE, aes(x=model_code, y=target, fill= round(MAE_diff_baseline,2))) + 
  geom_tile() +
  geom_text(aes(label=round(MAE)), size = 6) +
  scale_fill_gradient2(low = "blue2",
  high = "red", midpoint = 0,  name = "% change from baseline") + 
  xlab("Scored Models") + ylab("Forecast Target") +
  theme(axis.text.x =  element_text(angle = 45, hjust = 1, size = 16), 
        axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.title.x=element_blank()) + 
  facet_wrap( ~ mae_modelnum, ncol = 1) +
  guides(fill = FALSE) + 
  ggtitle("Predicted MAE")
```

```{r Panel 2A: Calc WIS}
average_byweek_calc$model_code <- reorder(average_byweek_calc$model_code, average_byweek_calc$avg_wis)

Strat_target_WIS_calc <- ggplot(average_byweek_calc, aes(x=model_code, y=target, fill= diff_baseline)) + 
  geom_tile() +
  geom_text(aes(label=round(avg_wis,0)), size = 6) +
  scale_fill_gradient2(low = "blue", high = "red", midpoint = 0, name = "% Change from baseline")+ 
  xlab("Scored model_codes") + 
  theme(axis.text.x =  element_text(angle = 45, hjust = 1, size = 16),
        axis.title.x=element_blank(),
        axis.text.y = element_text(size = 16)) +
  ggtitle("Calculated WIS")
```

```{r Panel 2B-D: pred WIS}
average_byweek_pred_wis$model_code <- reorder(average_byweek_pred_wis$model_code, average_byweek_pred_wis$wis)

Strat_target_wis_pred <- ggplot(average_byweek_pred_wis, aes(x=model_code, y=target, fill= round(wis_diff_baseline,2))) + 
  geom_tile() +
  geom_text(aes(label=round(wis)), size = 6) +
  scale_fill_gradient2(low = "blue2",
  high = "red", midpoint = 0,  name = "% change from baseline") + 
  xlab("Scored Models") + ylab("Forecast Target") +
  theme(axis.text.x =  element_text(angle = 45, hjust = 1, size = 16), 
        axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.title.x=element_blank()) + 
  facet_wrap( ~ wis_modelnum, ncol = 1) +
  ggtitle("Predicted WIS")
```

```{r, fig.width= 15, fig.height= 20}
gridExtra::grid.arrange(Strat_target_MAE_calc, Strat_target_WIS_calc,  Strat_target_MAE_pred, Strat_target_wis_pred)
```


#Figure 3: average performance of each model by location (emperical estimates)
```{r df for figure 3 }
location_fig3 <- empirical_df %>%
  filter(n_weeks_all_horizon == 14) %>%
  filter(n_location >= 25) %>%
  anti_join(dates_to_filter) %>%  ungroup() 

average_by_loc_calc <- location_fig3 %>%
  group_by(model_code, location_name) %>% 
  summarise(MAE  = round(mean(abs_error),1),        #calc MAE
        n_obs_ae = sum(abs_error),          #sanity check (not used in graph)
        avg_wis = round(mean(wis),1),    #calc WIS       
        n_obs_int=sum(wis)) %>% 
  group_by(location_name) %>%     
mutate_at(vars(matches("MAE")), funs(diff_baseline_MAE = (((.- .[model_code=="COVIDhub-baseline"]) / .[model_code=="COVIDhub-baseline"])*100))) %>%   #calculate MAE % change from baseline
mutate_at(vars(matches("avg_wis")), funs(diff_baseline_wis = (((.- .[model_code=="COVIDhub-baseline"]) / .[model_code=="COVIDhub-baseline"])*100))) %>% 
mutate_at(vars(matches("MAE")), funs(relative_basemae = (. / .[model_code=="COVIDhub-baseline"]))) %>%
mutate_at(vars(matches("avg_wis")), funs(relative_basewis = (./ .[model_code=="COVIDhub-baseline"]))) %>%
  ungroup()
```

```{r plot figure 3a MAE, fig.width=18, fig.height=10}
average_by_loc_calc$model_code <- reorder(average_by_loc_calc$model_code, average_by_loc_calc$MAE) #sort models by MAE for plot
average_by_loc_calc$location_name <- reorder(average_by_loc_calc$location_name, average_by_loc_calc$MAE)

ggplot(average_by_loc_calc, aes(x=model_code, y=location_name, fill= diff_baseline_MAE)) +
  geom_tile() +
  geom_text(aes(label=round(MAE))) +
  scale_fill_gradient2(low = "navy", high = "red", name = "% Change from baseline")+ 
  xlab("Scored Models") + ylab("Location") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

```{r plot figure 3b WIS, fig.width=18, fig.height=10}

average_by_loc_calc$model_code <- reorder(average_by_loc_calc$model_code, average_by_loc_calc$avg_wis) #sort models by MAE for plot
average_by_loc_calc$location_name <- reorder(average_by_loc_calc$location_name, average_by_loc_calc$avg_wis)


ggplot(average_by_loc_calc, aes(x=model_code, y=location_name, fill= diff_baseline_wis)) +
  geom_tile() +
  geom_text(aes(label=round(avg_wis))) +
  scale_fill_gradient2(low = "navy", high = "red", name = "% Change from baseline")+ 
  xlab("Scored Models") + ylab("Location") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```



#Figure 4: average performance of each model by week (averaged across locations, not imputed for weeks that are missing)

```{r}
myColors_cum <- c("black", "cyan2", "firebrick3",
                  "goldenrod4", "darkgreen", "brown2", 
                  "blue4", "darkorchid", "cadetblue2", 
                  "seagreen3", "red",  "darkgoldenrod1", 
                  "brown", "deeppink1", "darkorange")

names(myColors_cum) <- c("COVIDhub-baseline", "Teal", "Ruby",
                         "Goldenrod", "Emerald", "Scarlet", 
                         "Indigo", "Purple", "Aqua",
                         "Green",  "Red",  "Gold",  
                         "Maroon", "Pink", "Orange")

colScale_cum <- scale_colour_manual(name = "model_code", values = myColors_cum)
```

```{r}
average_byweek_calc <- empirical_df %>%
  filter(n_location == 51) %>%
  filter(n_horizons == 4) %>%
  group_by(model_code, first_fcast_sat) %>%
  summarise(mae = round(mean(abs_error, na.rm = T), 1),
        n_obs_ae = sum(!is.na(abs_error)), 
        avg_wis = round(mean(wis, na.rm=TRUE),1), 
        n_obs_int=sum(!is.na(wis))) %>% 
   group_by(first_fcast_sat) %>%
  mutate_at(vars(ends_with("MAE")), funs(relative_basewis = ((. - .[model_code=="COVIDhub-baseline"]) / .[model_code=="COVIDhub-baseline"])*100)) %>%
  mutate_at(vars(ends_with("avg_wis")), funs(relative_basemae = ((. - .[model_code=="COVIDhub-baseline"]) / .[model_code=="COVIDhub-baseline"])*100)) %>%
  ungroup() %>% arrange(first_fcast_sat, model_code)
```


```{r Figure 4 Panel 1A}
#Plot of MAE stratified by submission week
week_MAE <- ggplot(average_byweek_calc, aes(x= lubridate::ymd(first_fcast_sat), y=mae, color = model_code, fill = model_code)) +
  scale_x_date(date_labels = "%Y-%m-%d", breaks = c(first_fcast_sat)) + 
  geom_line() + 
  colScale_cum +
  geom_point(size = 2) + 
  xlab("1 Week Ahead Target Date") + ylab(NULL) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 15)) +
  ggtitle("MAE")
```


```{r Figure 4 Panel 2A}
week_mae_relative <- ggplot(average_byweek_calc, aes(x= lubridate::ymd(first_fcast_sat), y=relative_basemae, color = model_code, fill = model_code)) +
  scale_x_date(date_labels = "%Y-%m-%d", breaks = c(first_fcast_sat)) +
  #scale_color_manual(values = colors2) +
   geom_line() + 
  colScale_cum +
  geom_point(size = 2, value = colors) + 
  xlab("1 week ahead target date") + ylab(NULL) + ggtitle("MAE relative to baseline") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 15))
```

```{r Panel 1B}
#Plot of MAE stratified by submission week
week_wis <- ggplot(average_byweek_calc, aes(x= lubridate::ymd(first_fcast_sat), y=avg_wis, color = model_code, fill = model_code)) +
  scale_x_date(date_labels = "%Y-%m-%d", breaks = c(first_fcast_sat)) + 
  geom_line() + 
  colScale_cum +
  geom_point(size = 2) + 
  xlab("1 Week Ahead Target Date") + ylab(NULL) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 15)) +
  ggtitle("WIS")
```

```{r Figure 4 Panel 2B}
week_wis_relative <- ggplot(average_byweek_calc, aes(x= lubridate::ymd(first_fcast_sat), y=relative_basewis, color = model_code, fill = model_code)) +
  scale_x_date(date_labels = "%Y-%m-%d", breaks = c(first_fcast_sat)) +
  #scale_color_manual(values = colors2) +
   geom_line() + 
  colScale_cum +
  geom_point(size = 2, value = colors) + 
 # xlab("1 week ahead target date") + ylab(NULL) + ggtitle("WIS relative to baseline") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 15))
```

```{r, fig.width= 10, fig.height= 15}
#gridExtra::grid.arrange(week_MAE, week_mae_relative, week_wis, week_wis_relative)
```


```{r}
#Incidence dataset
# inc_tmp <- do_zoltar_query(zoltar_connection, 
#                            project_url =  "https://zoltardata.com/api/project/44/",
#                            is_forecast_query = FALSE,
#                            models = the_models,
#                            units = the_locations,
#                            targets = the_targets_inc,
#                            timezeros = the_timezeros_inc, 
#                            scores = the_scores) %>%
#    left_join(fips, by=c("unit" = "location")) %>%
#   mutate(wis = (.01*interval_2+.025*interval_5+.05*interval_10+.1*interval_20+.15*interval_30+.2*interval_40+.25*interval_50+
#                   .3*interval_60+.35*interval_70+.40*interval_80+.45*interval_90+.5*interval_100)/12, na.rm = TRUE)  %>%
#   mutate(first_fcast_sat = get_next_saturday(timezero) + ifelse(wday(timezero)<=2,0,7))
```




