---
title: "Assessing predictive performance of models in the COVID-19 Forcast Hub"
author: "Estee Y Cramer, Nicholas G Reich, "
date: "`r Sys.Date()`"
output:
  rmdformats::html_clean:
    highlight: kate
    number_sections: no
    fig_width: 18
    fig_height: 10
---

#Prelims
```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE, echo = FALSE)
library(lubridate)
library(kableExtra)
library(tidyverse)
theme_set(theme_bw())
```

```{r global parameters}
## minimum number of weeks for eligibility
NUM_WEEKS_CUM <- 14
NUM_WEEKS_INC <- 11

## minumum number of models in a week to be considered eligible
NUM_UNITS <- 25
```

```{r read in other files to be used later}

## stan model files
stan_model_ae <- readRDS("../paper-inputs/20200927-stan-fit-scores-negbin.rds")

## read score files
cum_scores <- read_csv("../paper-inputs/20201013-cum-scores.csv")

inc_scores <- read_csv("../paper-inputs/20201013-inc-scores.csv")

## read model eligibility file
model_eligibility <- read_csv("../paper-inputs/model-eligibility.csv")

## locations/dates with reporting anomalies
dates_to_filter <- read_csv("../paper-inputs/anomaly-reporting-dates.csv") %>%
  filter(to_remove==1)
```

```{r add blinded model code}
possible_colors <- c("Purple", "Aqua", "Green", "Gray", "Red", "Gold", "Pink", 
  "Goldenrod", "Maroon", "Indigo", "Orange", "Teal", "Emerald", "Lilac", 
  "Tan", "Scarlet", "Ruby")

cum_scores$model_code <- factor(cum_scores$model, labels=sample(possible_colors, size = length(unique(cum_scores$model)), replace = FALSE)) 

inc_scores$model_code <- factor(inc_scores$model, labels=sample(possible_colors, size = length(unique(inc_scores$model)), replace = FALSE))

#change baseline model_code to baseline
cum_scores <- cum_scores %>%
  mutate(model_code = ifelse(model == "COVIDhub-baseline", "COVIDhub-baseline", as.character(model_code))) %>%
  mutate(model_code = as.factor(model_code))

inc_scores <- inc_scores %>%
  mutate(model_code = ifelse(model == "COVIDhub-baseline", "COVIDhub-baseline", as.character(model_code))) %>%
  mutate(model_code = as.factor(model_code))
```


```{r filter to 4 targets}
cum_scores_calc <- cum_scores %>%
  filter(target %in% c("1 wk ahead cum death", "2 wk ahead cum death", "3 wk ahead cum death", "4 wk ahead cum death")) #keep only targets 1-4

inc_scores_calc <- inc_scores %>%
  filter(target %in% c("1 wk ahead inc death", "2 wk ahead inc death", "3 wk ahead inc death", "4 wk ahead inc death")) 
```

```{r include missing combinations}

#Cumulative Missing Combos: 

#list all combinations
missing_combos <- cum_scores_calc %>%
  tidyr::expand(model_code, target_end_date_1wk_ahead, location_name, target)

#fill in missing combinations into main dataset 
cum_scores_calc1 <- cum_scores_calc %>%
  right_join(missing_combos)

#merge with dates to filter to remove locations with backfilled weeks
cum_scores_calc2 <- cum_scores_calc1 %>%
  left_join(dates_to_filter) %>%
  filter((target_end_date_1wk_ahead > first_fcast_date_impacted + 4) | is.na(first_fcast_date_impacted) | is.na(target_end_date_1wk_ahead))


#Incident Missing Combos: 
#list all combinations
missing_combos_inc <- inc_scores_calc %>%
  tidyr::expand(model_code, target_end_date_1wk_ahead, location_name, target)

#fill in missing combinations into main dataset 
inc_scores_calc1 <- inc_scores_calc %>%
  right_join(missing_combos_inc)

#merge with dates to filter to remove locations with backfilled weeks
inc_scores_calc2 <- inc_scores_calc1 %>%
  left_join(dates_to_filter) %>%
  filter((target_end_date_1wk_ahead > first_fcast_date_impacted + 4) | is.na(first_fcast_date_impacted) | is.na(target_end_date_1wk_ahead))
```

#Figure 2: Model Performance stratified by target (aggregated by week and location): emperical and calculated values
```{r Figure 2: Calculated Cumulative Deaths Stratified by Target Week, fig.width= 12, fig.height=10}
avg_bytarget_calc <- cum_scores_calc2 %>%
  filter(location_name %in% c("United States", datasets::state.name)) %>%
 group_by(model_code, target) %>%
  summarise(MAE  = round(mean(abs_error, na.rm = F),1),  #calc MAE
        n_obs_ae=sum(abs_error),
         avg_wis = round(mean(wis),1),       #calc wis
        n_obs_int=sum(wis)) %>%    #sanity check count
  ungroup() %>%
  group_by(target) %>%
  mutate_at(vars(MAE), funs(percent_change_baseline_MAE = (((.- .[model_code=="COVIDhub-baseline"]) / .[model_code =="COVIDhub-baseline"])*100))) %>%
  mutate_at(vars(avg_wis), funs(percent_change_baseline_WIS = (((.- .[model_code =="COVIDhub-baseline"]) / .[model_code =="COVIDhub-baseline"])*100))) %>%
  ungroup()

#MAE with calculated data
avg_bytarget_calc$model_code <- reorder(avg_bytarget_calc$model_code, avg_bytarget_calc$MAE)

ggplot(avg_bytarget_calc, aes(x=model_code, y=target, fill= percent_change_baseline_MAE)) + 
  geom_tile() +
  geom_text(aes(label=round(MAE)), size = 6) +
  scale_fill_gradient2(low = "blue2",
  high = "red", midpoint = 0,  name = "% Change from baseline") + 
  xlab("Scored Models") + ylab("Forecast Target") +
  theme(axis.text.x =  element_text(angle = 45, hjust = 1, size = 16),
        axis.title.x=element_blank(),
        axis.text.y = element_text(size = 16)) +
  ggtitle("Calculated MAE")

#WIS with calculated data
avg_bytarget_calc$model_code <- reorder(avg_bytarget_calc$model_code, avg_bytarget_calc$avg_wis)

ggplot(avg_bytarget_calc, aes(x=model_code, y=target, fill= percent_change_baseline_WIS)) + 
  geom_tile() +
  geom_text(aes(label=round(avg_wis,0)), size = 6) +
  scale_fill_gradient2(low = "blue", high = "red", midpoint = 0, name = "% Change from baseline")+ 
  xlab("Scored model_codes") + 
  theme(axis.text.x =  element_text(angle = 45, hjust = 1, size = 16),
        axis.title.x=element_blank(),
        axis.text.y = element_text(size = 16)) +
  ggtitle("Calculated WIS")
```

```{r Figure 2 continued: Predicted MAE and WIS from stan model, fig.width= 12, fig.height=10}
stan_ae_df <- broom::tidy(stan_model_ae)

model_df <- stan_ae_df[2:16,1:2]
names(model_df) <- c("model_code", "MC_coef")

week_df <- stan_ae_df[17:19,1:2]
week_df <- week_df[rep(seq_len(nrow(week_df)), each = 15), ]

interaction_df <- stan_ae_df[20:64,1:2]

m_df_coef <- cbind(model_df, week_df, interaction_df)

colnames(m_df_coef) <- c("model_code", "MC_coef", "target", "target_coef", "interaction", "interaction_coef")

m_df_coef <- bind_rows(m_df_coef, model_df)

baseline0 <- data.frame("COVIDhub-baseline",0, "target1 wk ahead cum death", 0, "none", 0)
baseline1 <- data.frame("COVIDhub-baseline",0,  "target2 wk ahead cum death", stan_ae_df$estimate[stan_ae_df$term == "target2 wk ahead cum death"], "none", 0)
baseline2 <- data.frame("COVIDhub-baseline",0, "target3 wk ahead cum death", stan_ae_df$estimate[stan_ae_df$term == "target3 wk ahead cum death"], "none", 0)
baseline3 <- data.frame("COVIDhub-baseline",0, "target4 wk ahead cum death", stan_ae_df$estimate[stan_ae_df$term == "target4 wk ahead cum death"], "none", 0)

names(baseline0) <- names(m_df_coef)
names(baseline1) <- names(m_df_coef)
names(baseline2) <- names(m_df_coef)
names(baseline3) <- names(m_df_coef)

m_df_coef <- rbind(baseline0,baseline1,baseline2,baseline3,m_df_coef) %>%
  mutate(target = replace_na(target, "target1 wk ahead cum death")) %>%
  rowwise() %>%
  mutate(total_coef = sum(MC_coef , target_coef , interaction_coef, na.rm = TRUE)) %>%
  mutate(model_code = str_remove(model_code, "model_code")) %>%
  mutate(target = str_remove(target, "ahead cum death"))

ggplot(m_df_coef, aes(x=model_code, y=target, fill= total_coef)) + 
  geom_tile() +
  geom_text(aes(label=round(total_coef, 2)), size = 10) +
  scale_fill_gradient2(low = "blue2",
  high = "red", midpoint = 1,  name = "% change from baseline") + 
  xlab("Scored Models") + ylab("Forecast Target") +
  theme(axis.text.x =  element_text(angle = 45, hjust = 1, size = 20),
        axis.title.x=element_blank(),
        axis.text.y = element_text(size = 20)) +
  guides(fill = FALSE) + 
  ggtitle("Absolute Error model coefficients from STAN")
```


#Figure 3: average performance of each model by location (emperical estimates)
```{r Figure 3: aggregate by location mae, fig.width=18, fig.height=10}
avg_byloc_calc <- cum_scores_calc2  %>%
  group_by(model_code, location_name) %>% 
  summarise(MAE  = round(mean(abs_error),1),        #calc MAE
        n_obs_ae = sum(abs_error),          #sanity check (not used in graph)
        avg_wis = round(mean(wis),1),    #calc WIS       
        n_obs_int=sum(wis)) %>% 
  group_by(location_name) %>%     
  mutate_at(vars(MAE), funs(percent_change_baseline_MAE = (((.- .[model_code=="COVIDhub-baseline"]) / .[model_code =="COVIDhub-baseline"])*100))) %>%
  mutate_at(vars(avg_wis), funs(percent_change_baseline_WIS = (((.- .[model_code =="COVIDhub-baseline"]) / .[model_code =="COVIDhub-baseline"])*100))) %>%
  ungroup()

#Figure 3: MAE scores
avg_byloc_calc$model_code <- reorder(avg_byloc_calc$model_code, avg_byloc_calc$MAE, na.rm = T) #sort models by MAE for plot
avg_byloc_calc$location_name <- reorder(avg_byloc_calc$location_name, avg_byloc_calc$MAE, na.rm = T)

ggplot(avg_byloc_calc, aes(x=model_code, y=location_name, fill= percent_change_baseline_MAE)) +
  geom_tile() +
  geom_text(aes(label=round(MAE))) +
  scale_fill_gradient2(low = "navy", high = "red", name = "% Change from baseline")+ 
  xlab("Scored Models") + ylab("Location") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

#Figure 3: WIS scores 
avg_byloc_calc$model_code <- reorder(avg_byloc_calc$model_code, avg_byloc_calc$avg_wis, na.rm = T) #sort models by MAE for plot
avg_byloc_calc$location_name <- reorder(avg_byloc_calc$location_name, avg_byloc_calc$avg_wis, na.rm = T)

ggplot(avg_byloc_calc, aes(x=model_code, y=location_name, fill= percent_change_baseline_WIS)) +
  geom_tile() +
  geom_text(aes(label=round(avg_wis))) +
  scale_fill_gradient2(low = "navy", high = "red", name = "% Change from baseline")+ 
  xlab("Scored Models") + ylab("Location") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```


#Figure 4: average performance of each model by week (averaged across locations, not imputed for weeks that are missing)
```{r add color scheme to hide model names}
myColors_cum <- c("black", "cyan2", "firebrick3",
                  "goldenrod4", "darkgreen", "brown2", 
                  "blue4", "darkorchid", "cadetblue2", 
                  "seagreen3", "red",  "darkgoldenrod1", 
                  "brown", "deeppink1", "darkorange", "wheat3", "plum2")

names(myColors_cum) <- c("COVIDhub-baseline", "Teal", "Ruby",
                         "Goldenrod", "Emerald", "Scarlet", 
                         "Indigo", "Purple", "Aqua",
                         "Green",  "Red",  "Gold",  
                         "Maroon", "Pink", "Orange", "Tan", "Lilac") 

colScale_cum <- scale_colour_manual(name = "model_code", values = myColors_cum)
```

```{r Figure 4: models strat by week, fig.height= 8, fig.width= 10}
avg_byweek_calc <- cum_scores_calc2 %>%
  filter(location_name %in% c("United States ", datasets::state.name)) %>%
  group_by(model_code, target_end_date_1wk_ahead) %>%
  summarise(MAE = round(mean(abs_error), 1),
        n_obs_ae = sum(abs_error), 
        avg_wis = round(mean(wis),1), 
        n_obs_int=sum(wis)) %>% 
   group_by(target_end_date_1wk_ahead) %>%
  mutate_at(vars(MAE), funs(percent_change_baseline_MAE = (((.- .[model_code=="COVIDhub-baseline"]) / .[model_code =="COVIDhub-baseline"])*100))) %>%
  mutate_at(vars(avg_wis), funs(percent_change_baseline_WIS = (((.- .[model_code =="COVIDhub-baseline"]) / .[model_code =="COVIDhub-baseline"])*100))) %>%
  mutate_at(vars(MAE), funs(relative_MAE = (. / .[model_code =="COVIDhub-baseline"]))) %>%
  mutate_at(vars(avg_wis), funs(relative_WIS = (. / .[model_code =="COVIDhub-baseline"]))) %>%
  ungroup() %>% arrange(target_end_date_1wk_ahead, model_code)


#Plot of MAE stratified by submission week
ggplot(avg_byweek_calc, aes(x= lubridate::ymd(target_end_date_1wk_ahead), y=MAE, color = model_code, fill = model_code)) +
  scale_x_date(date_labels = "%Y-%m-%d", breaks = c(avg_byweek_calc$target_end_date_1wk_ahead)) + 
  geom_line() + 
  colScale_cum +
  geom_point(size = 2) + 
  xlab("1 Week Ahead Target Date") + ylab(NULL) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 15)) +
  ggtitle("MAE")

#Figure 4: Relative MAE
ggplot(avg_byweek_calc, aes(x= lubridate::ymd(target_end_date_1wk_ahead), y=relative_MAE, color = model_code, fill = model_code)) +
  scale_x_date(date_labels = "%Y-%m-%d", breaks = c(avg_byweek_calc$target_end_date_1wk_ahead)) +
  #scale_color_manual(values = colors2) +
   geom_line() + 
  colScale_cum +
  geom_point(size = 2, value = colors) + 
  xlab("1 week ahead target date") + ylab(NULL) + ggtitle("MAE relative to baseline") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 15))

#Figure 4: average WIS
ggplot(avg_byweek_calc, aes(x= lubridate::ymd(target_end_date_1wk_ahead), y=avg_wis, color = model_code, fill = model_code)) +
  scale_x_date(date_labels = "%Y-%m-%d", breaks = c(avg_byweek_calc$target_end_date_1wk_ahead)) + 
  geom_line() + 
  colScale_cum +
  geom_point(size = 2) + 
  xlab("1 Week Ahead Target Date") + ylab(NULL) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 15)) +
  ggtitle("WIS")

#Figure 4: relative WIS
ggplot(avg_byweek_calc, aes(x= lubridate::ymd(target_end_date_1wk_ahead), y=relative_WIS, color = model_code, fill = model_code)) +
  scale_x_date(date_labels = "%Y-%m-%d", breaks = c(avg_byweek_calc$target_end_date_1wk_ahead)) +
   geom_line() + 
  colScale_cum +
  geom_point(size = 2, value = colors) + 
  xlab("1 week ahead target date") + ylab(NULL) + ggtitle("WIS relative to baseline") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 15))
```

#Figure 5: Average performance of incident models by target 
```{r Figure 5: Calculated Incident Deaths Stratified by Target Week, fig.width= 10, fig.height=10}
avg_bytarget_calc_inc <- inc_scores_calc2 %>%
  filter(location_name %in% c("United States", datasets::state.name)) %>%
 group_by(model_code, target) %>%
  summarise(MAE  = round(mean(abs_error, na.rm = F),1),  #calc MAE
        n_obs_ae=sum(abs_error),
         avg_wis = round(mean(wis),1),       #calc wis
        n_obs_int=sum(wis)) %>%    #sanity check count
  ungroup() %>%
  group_by(target) %>%
  mutate_at(vars(MAE), funs(percent_change_baseline_MAE = (((.- .[model_code=="COVIDhub-baseline"]) / .[model_code =="COVIDhub-baseline"])*100))) %>%
  mutate_at(vars(avg_wis), funs(percent_change_baseline_WIS = (((.- .[model_code =="COVIDhub-baseline"]) / .[model_code =="COVIDhub-baseline"])*100))) %>%
  ungroup() 

#MAE with calculated data
avg_bytarget_calc_inc$model_code <- reorder(avg_bytarget_calc_inc$model_code, avg_bytarget_calc_inc$MAE)

ggplot(avg_bytarget_calc_inc, aes(x=model_code, y=target, fill= percent_change_baseline_MAE)) + 
  geom_tile() +
  geom_text(aes(label=round(MAE)), size = 6) +
  scale_fill_gradient2(low = "blue2",
  high = "red", midpoint = 0,  name = "% change from baseline") + 
  xlab("Scored Models") + ylab("Forecast Target") +
  theme(axis.text.x =  element_text(angle = 45, hjust = 1, size = 16),
        axis.title.x=element_blank(),
        axis.text.y = element_text(size = 16)) +
  ggtitle("Calculated MAE")

#WIS with calculated data
avg_bytarget_calc_inc$model_code <- reorder(avg_bytarget_calc_inc$model_code, avg_bytarget_calc_inc$avg_wis)

ggplot(avg_bytarget_calc_inc, aes(x=model_code, y=target, fill= percent_change_baseline_WIS)) + 
  geom_tile() +
  geom_text(aes(label=round(avg_wis,0)), size = 6) +
  scale_fill_gradient2(low = "blue", high = "red", midpoint = 0, name = "% Change from baseline")+ 
  xlab("Scored model_codes") + 
  theme(axis.text.x =  element_text(angle = 45, hjust = 1, size = 16),
        axis.title.x=element_blank(),
        axis.text.y = element_text(size = 16)) +
  ggtitle("Calculated WIS")
```


#Figure 6: average performance of each model by location (Incident Deaths)
```{r Figure 6: aggregate by location for incident deaths, fig.width=18, fig.height=10}
avg_byloc_calc_inc <- inc_scores_calc2  %>%
  group_by(model_code, location_name) %>% 
  summarise(MAE  = round(mean(abs_error),1),        #calc MAE
        n_obs_ae = sum(abs_error),          #sanity check (not used in graph)
        avg_wis = round(mean(wis),1),    #calc WIS       
        n_obs_int=sum(wis)) %>% 
  group_by(location_name) %>%     
  mutate_at(vars(MAE), funs(percent_change_baseline_MAE = (((.- .[model_code=="COVIDhub-baseline"]) / .[model_code =="COVIDhub-baseline"])*100))) %>%
  mutate_at(vars(avg_wis), funs(percent_change_baseline_WIS = (((.- .[model_code =="COVIDhub-baseline"]) / .[model_code =="COVIDhub-baseline"])*100))) %>%
  ungroup()

#Figure 6: MAE scores inc
avg_byloc_calc_inc$model_code <- reorder(avg_byloc_calc_inc$model_code, avg_byloc_calc_inc$MAE) #sort models by MAE for plot
avg_byloc_calc_inc$location_name <- reorder(avg_byloc_calc_inc$location_name, avg_byloc_calc_inc$MAE, na.rm = F)

ggplot(avg_byloc_calc_inc, aes(x=model_code, y=location_name, fill= percent_change_baseline_MAE)) +
  geom_tile() +
  geom_text(aes(label=round(MAE))) +
  scale_fill_gradient2(low = "navy", high = "red", name = "% Change from baseline")+ 
  xlab("Scored Models") + ylab("Location") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

#Figure 6: WIS scores inc
avg_byloc_calc_inc$model_code <- reorder(avg_byloc_calc_inc$model_code, avg_byloc_calc_inc$avg_wis) 
avg_byloc_calc_inc$location_name <- reorder(avg_byloc_calc_inc$location_name, avg_byloc_calc_inc$avg_wis, na.rm = T)

ggplot(avg_byloc_calc_inc, aes(x=model_code, y=location_name, fill= percent_change_baseline_WIS)) +
  geom_tile() +
  geom_text(aes(label=round(avg_wis))) +
  scale_fill_gradient2(low = "navy", high = "red", name = "% Change from baseline") + 
  xlab("Scored Models") + ylab("Location") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

#Figure 7 Average performance stratified by week of submission
```{r Figure 7: Models aggregated by target and location Inc, fig.height= 8, fig.width= 10}
avg_byweek_calc_inc <- inc_scores_calc2 %>%
  filter(location_name %in% c("United States ", datasets::state.name)) %>%
  group_by(model_code, target_end_date_1wk_ahead) %>%
  summarise(MAE = round(mean(abs_error), 1),
        n_obs_ae = sum(abs_error), 
        avg_wis = round(mean(wis),1), 
        n_obs_int=sum(wis)) %>% 
   group_by(target_end_date_1wk_ahead) %>%
  mutate_at(vars(MAE), funs(percent_change_baseline_MAE = (((.- .[model_code=="COVIDhub-baseline"]) / .[model_code =="COVIDhub-baseline"])*100))) %>%
  mutate_at(vars(avg_wis), funs(percent_change_baseline_WIS = (((.- .[model_code =="COVIDhub-baseline"]) / .[model_code =="COVIDhub-baseline"])*100))) %>%
  mutate_at(vars(MAE), funs(relative_MAE = (. / .[model_code =="COVIDhub-baseline"]))) %>%
  mutate_at(vars(avg_wis), funs(relative_WIS = (. / .[model_code =="COVIDhub-baseline"]))) %>%
  ungroup() %>% arrange(target_end_date_1wk_ahead, model_code)


#Plot of MAE stratified by submission week
ggplot(avg_byweek_calc_inc, aes(x= lubridate::ymd(target_end_date_1wk_ahead), y=MAE, color = model_code, fill = model_code)) +
  scale_x_date(date_labels = "%Y-%m-%d", breaks = c(avg_byweek_calc_inc$target_end_date_1wk_ahead)) + 
  geom_line() + 
  colScale_cum +
  geom_point(size = 2) + 
  xlab("1 Week Ahead Target Date") + ylab(NULL) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 15)) +
  ggtitle("MAE")

#Figure 4: Relative MAE
ggplot(avg_byweek_calc_inc, aes(x= lubridate::ymd(target_end_date_1wk_ahead), y=relative_MAE, color = model_code, fill = model_code)) +
  scale_x_date(date_labels = "%Y-%m-%d", breaks = c(avg_byweek_calc_inc$target_end_date_1wk_ahead)) +
  #scale_color_manual(values = colors2) +
   geom_line() + 
  colScale_cum +
  geom_point(size = 2, value = colors) + 
  xlab("1 week ahead target date") + ylab(NULL) + ggtitle("MAE relative to baseline") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 15))

#Figure 4: average WIS
ggplot(avg_byweek_calc_inc, aes(x= lubridate::ymd(target_end_date_1wk_ahead), y=avg_wis, color = model_code, fill = model_code)) +
  scale_x_date(date_labels = "%Y-%m-%d", breaks = c(avg_byweek_calc_inc$target_end_date_1wk_ahead)) + 
  geom_line() + 
  colScale_cum +
  geom_point(size = 2) + 
  xlab("1 Week Ahead Target Date") + ylab(NULL) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 15)) +
  ggtitle("WIS")

#Figure 4: relative WIS
ggplot(avg_byweek_calc_inc, aes(x= lubridate::ymd(target_end_date_1wk_ahead), y=relative_WIS, color = model_code, fill = model_code)) +
  scale_x_date(date_labels = "%Y-%m-%d", breaks = c(avg_byweek_calc_inc$target_end_date_1wk_ahead)) +
   geom_line() + 
  colScale_cum +
  geom_point(size = 2, value = colors) + 
  xlab("1 week ahead target date") + ylab(NULL) + ggtitle("WIS relative to baseline") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 15))
```
