---
title: "COVID-19 US Forecast Evaluation Report"
author: "This report was developed by the [Reich Lab](https://reichlab.io/) and the US [COVID-19 Forecast Hub](https://covid19forecasthub.org/) from UMass-Amherst in collaboration with [CMU Delphi](https://delphi.cmu.edu/), as part of the Forecast Evaluation Research Collaborative."
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
      
---
<!-- code to run rmarkdown::render(input="./vignettes/covidHubUtils-overview.Rmd") -->

<!-- Code for adding logo at the top -->

<!-- <script> -->
<!--   $(document).ready(function() { -->
<!--     $('#TOC').parent().prepend('<div id=\"nav_logo\"><a href=\"https://covid19forecasthub.org/\" target=\"_blank\"><img src=\"https://github.com/reichlab/covid19-forecast-hub-web/raw/master/images/forecast-hub-logo_DARKBLUE.png\"></a></div>'); -->
<!--   }); -->
<!-- </script> -->

<style>
#nav_logo {
  width: 100%;
  margin-top: 20px;
}

#TOC {
  background: url("https://github.com/reichlab/covid19-forecast-hub-web/raw/master/images/forecast-hub-logo_DARKBLUE-20px-padding.png");
  background-size: contain;
  padding-top: 80px !important;
  background-repeat: no-repeat;
}
</style>
<!-- </style> -->

```{r setup, include=FALSE}
#load libraries
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(lubridate)
library(scoringutils)
library(RColorBrewer)
library(DT)
library(surveillance)
library(htmltools)
library(kableExtra)
library(covidHubUtils)
library(plotly)
library(tidyverse)
library(zoltr)
library(dplyr)
theme_set(theme_bw())

source("functions_weekly_evaluation.R")
data("hub_locations")
```

```{r prelim set values}
# the_locations <- hub_locations %>% filter(geo_type == "state") %>%
#   filter(abbreviation %in% datasets::state.abb) %>% pull(fips) #states, us and territories

US_fips <- hub_locations %>%  filter(geo_type == "state") %>% filter(abbreviation %in% datasets::state.abb) %>% pull(fips) #only 50 states 

n_weeks_ohio <- 4 #weeks to exclude truth data for ohio
n_weeks_eval <- 10 #weeks included in evaluation
n_weeks_submitted <- 5 #number of weeks needed for inclusion if no longer submitting
n_weeks_history <- 26 # number of weeks for historical data
```

```{r get-date-boundaries}
#Important dates used
forecast_mon <- lubridate::floor_date(Sys.Date(), unit = "week") + 1      #Even when running on Tuesday, will be Monday date
last_eval_sat <- as.Date(calc_target_week_end_date(forecast_mon, horizon = 0))
first_eval_sat <- last_eval_sat  - 7*(n_weeks_eval - 1)  #First Evaluated Date
first_eval_sat_ohio <- last_eval_sat  - 7*(n_weeks_ohio - 1)  #First week to exclude truth data for Ohio
first_eval_sat_hist <- last_eval_sat  - 7*(n_weeks_history - 1)  #First Evaluated Date (historical)

last_submission_date <- last_eval_sat  - 5 #Last submission date
first_submission_date <- first_eval_sat - 11  #First submission date

first_mon_cutoff <- first_eval_sat - 5

last_1wk_target_end_date <- as.Date(calc_target_week_end_date(last_submission_date, horizon = 1)) #last 1 week ahead horizon
first_1wk_target_end_date  <- as.Date(calc_target_week_end_date(first_submission_date, horizon = 0)) #first 1 week ahead horizon

first_4wk_target_end_date  <- as.Date(calc_target_week_end_date(first_submission_date, horizon = 4)) #first horizon with all 4 target weeks evaluated 
last_4wk_target_end_date <- as.Date(calc_target_week_end_date(last_submission_date, horizon = 4))

eval_sat <- c(first_eval_sat, last_eval_sat) #range of dates evaluated 
```


```{r load data}
#load files generated in query-scores-weekly-report.R
load(file = "truth_dat_case.rda")
load(file = "truth_dat_inc.rda")
load(file = "truth_dat_hosp.rda")
load(file = "truth_dat_case_all.rda")
load(file = "truth_dat_inc_all.rda")
load(file = "truth_dat_hosp_all.rda")
load(file = "score_case_all.rda") 
load(file = "score_inc_all.rda") 
load(file = "score_hosp_all.rda") 

# remove COVIDhub-4_week_ensemble model from cases and deaths for now 
score_inc_all <- score_inc_all  %>% filter(model != "COVIDhub-4_week_ensemble")
score_case_all <- score_case_all  %>% filter(model != "COVIDhub-4_week_ensemble")


# remove most recent 4 weeks of truth/score for ohio
truth_dat_inc_all_ohio <- truth_dat_inc_all  %>%
  subset((location != "39") | (location == "39" & target_end_date < first_eval_sat_ohio))

truth_dat_inc_ohio <- truth_dat_inc  %>%
  subset((location != "39") | (location == "39" & target_end_date < first_eval_sat_ohio))

score_inc_all_ohio <- score_inc_all  %>%
  subset((location != "39") | (location == "39" & target_end_date < first_eval_sat_ohio))




```


```{r}
location_order_case <- truth_dat_case %>% 
  filter(target_end_date == max(target_end_date)) %>%
  arrange(value) %>%
  pull(location_name)

location_order_death <- truth_dat_inc %>% 
  filter(target_end_date == max(target_end_date)) %>%
  arrange(value) %>%
  pull(location_name)

location_order_hosp <- truth_dat_hosp %>% 
  filter(target_end_date == max(target_end_date)) %>%
  arrange(value) %>%
  pull(location_name)
  
```


```{r inclusion in accuracy table historical}
#at least 50% of historical WIS or historical MAE
case_accuracy_historical <- historical_accuracy_filter(score_case_all)
inc_accuracy_historical <- historical_accuracy_filter(score_inc_all_ohio)
hosp_accuracy_historical <- historical_accuracy_filter(score_hosp_all)
```



# Overview
This report provides an evaluation of the accuracy and precision of probabilistic forecasts of COVID-19 cases and deaths submitted to the [US COVID-19 Forecast Hub](https://covid19forecasthub.org/). Some analyses include forecasts submitted in the past six months, starting in `r format(first_eval_sat_hist, "%B %d, %Y")`. Others focus on evaluating "recent" forecasts, submitted only in the last `r n_weeks_eval` weeks. 

<!-- The forecasts evaluated were submitted during the time period from `r format(first_submission_date, "%B %d, %Y")` through `r format(last_submission_date, "%B %d, %Y")`. The revision dates of this data was calculated as of `r today()`.
In this weekly report we are evaluating forecasts made in 57 different locations (US on a national level, 50 states, and 6 territories), for 4 horizons over `r n_weeks_eval` submission weeks. We are evaluating incident cases, and incident deaths. 

Additionally, we have included a historical score report to aggregate scores from forecasts that have been submitted to the forecast hub since the first week in April.
-->

In collaboration with the US Centers for Disease Control and Prevention (CDC), the COVID-19 Forecast hub collects short-term COVID-19 forecasts from dozens of research groups around the globe. Every week we combine the most recent forecasts from each team into a single "ensemble" forecast for each of the targets. This forecast is used as the official ensemble forecast of the CDC, typically appearing on their [forecasting website](https://www.cdc.gov/coronavirus/2019-ncov/covid-data/mathematical-modeling.html) on Wednesday.  You can explore the full set of models, including their forecasts for past weeks online at CDC's [interactive forecast visualization](https://covid.cdc.gov/covid-data-tracker/#forecasting_weeklydeaths/).  Other related resources include CMU Delphi's [forecast evaluation dashboard](https://delphi.cmu.edu/forecast-eval/), a separate product of the Forecast Evaluation Research Collaborative, as well as the preprint [Evaluation of individual and ensemble probabilistic forecasts of COVID-19 mortality in the US.](https://www.medrxiv.org/content/10.1101/2021.02.03.21250974v2)

This report evaluates forecasts at the state and national level for newly reported weekly cases and deaths due to COVID-19. Data from the [JHU CSSE dashboard](https://coronavirus.jhu.edu/) is used as ground truth data for evaluating the forecasts.

We evaluate models based on their [adjusted relative weighted interval scores (WIS, a measure of distributional accuracy)](https://journals.plos.org/ploscompbiol/article?id=10.1371/journal.pcbi.1008618), and adjusted relative mean absolute error (MAE). Scores are aggregated separately for the most recent 10 weeks and for 26 historical weeks. To account for the variation in difficult of forecasting different weeks and locations, a [pairwise approach](https://www.medrxiv.org/content/10.1101/2021.02.03.21250974v2) was used to calculated the relative adjusted WIS and MAE. Models with relative scores lower than 1 have been more accurate than the baseline on average, whereas relative scores greater than 1 indicate less accuracy than baseline on average.


# Incident Case Forecasts {.tabset .tabset-fade}

## Summary Tables {.tabset .tabset-fade}

The first and second tables evaluate recent/historical forecast models based on their WIS and MAE by horizon.  

The third and fourth tables evaluate recent/historical forecast models based on their prediction interval coverage at the 50% and 95% levels by horizon. 

Scores are aggregated separately for the most recent 10 weeks and for 26 historical weeks. 

<!-- * The **prediction interval coverage**  measures  the proportion of times a prediction interval of a certain level covered the true value, to assess the degree to which forecasts accurately characterized uncertainty about future observations. Well calibrated models should have a 50% coverage level of 0.5 and a 95% coverage level of 0.95. 

* The **weighted interval score (WIS)** is a proper score that combines a set of interval scores for probabilistic forecasts that provide quantiles of the predictive forecast distribution. To account for the variation in difficult of forecasting different weeks and locations, a pairwis approach was used to calculated the relative adjusted WIS. The code for this comparison can be found [here](https://github.com/jbracher/pairwise_comparisons). A preprint on this method for calculating the WIS can be found [here](https://arxiv.org/pdf/2005.12881.pdf). Models with an adjusted relative WIS  lower than 1 are more accurate than the baseline, and models with an adjusted relative WIS greater than 1 are less accurate than the baseline is predicting the number of incident cases. 

* The **mean absolute error** is defined as the the difference between the forecasted value and the actual value. For this calculation, point forecasts submitted by teams were used. When point forecasts were not available, the 0.50 quantile was used. Similar to calculating the WIS, a pairwise approach was used to account for variation across locations and weeks. Models with an adjusted relative MAE lower than 1 are more accurate than the baseline, and models with an adjusted relative MAE greater than 1 are less accurate than the baseline is predicting the number of incident cases. 
-->
 
Inclusion criteria for each column are detailed below the table. 


```{r recent relative wis  CASE}
#at least 50% of recent WIS or 50% of recent MAE
case_accuracy_recent <- recent_accuracy_filter(score_case_all)

inc_scores <- case_accuracy_recent %>%
  filter(!is.na(score_value)) %>%
  filter(n_locations >= 25) %>% 
  droplevels()

# bring all timezeros to Monday:
inc_scores$timezero <- inc_scores$submission_sat
# 
# restrict to 1-4 wk ahead state-level
scores <- inc_scores %>% filter(horizon %in% paste(1:4)) %>%
  filter(score_name %in% c("wis")) %>%
  select("model", "timezero", "location", "horizon", "score_name", "score_value") %>%
  pivot_wider(names_from = score_name, values_from = score_value) %>%
  filter(!is.na(wis)) %>%
  droplevels()

# the included models:
models <- unique(scores$model)

#pairwise comparison function
pairwise_comparison <- function(scores, mx, my, subset = rep(TRUE, nrow(scores)),
                                permutation_test = FALSE){
  # subsets of available scores for both models:
  subx <- subset(scores, model == mx)
  suby <- subset(scores, model == my)
  # merge together and restrict to overlap:
  sub <- merge(subx, suby, by = c("timezero", "location", "horizon"),
               all.x = FALSE, all.y = FALSE)
  ##### catch common problems:
  ##### no overlap between targets covered by x and y:
  if(nrow(sub) == 0){
    warning("No overlap of covered forecast targets for ", mx, "and", my, ". Returning NA.")
    return(list(ratio = NA, pval = NA, pval_fcd = NA, mx = mx, my = my))
  }
  ##### unavailable scores (likely because a model issues only point forecasts?)
  if(any(is.na(subx$wis))){
    warning("Some or all wis values are NA for ", mx, ". Returning NA.")
    return(list(ratio = NA, pval = NA, pval_fcd = NA, mx = mx, my = my))
  }
  if(any(is.na(suby$wis))){
    warning("Some or all wis values are NA for ", my, ". Returning NA.")
    return(list(ratio = NA, pval = NA, pval_fcd = NA, mx = mx, my = my))
  }

  # compute ratio:

  # matrices to store:
  results_ratio <- results_pval <- results_pval_fcd <- matrix(ncol = length(models),
                                                              nrow = length(models),
                                                              dimnames = list(models, models))

  ratio <- sum(sub$wis.x) / sum(sub$wis.y)
  # perform permutation tests:
  if(permutation_test){
    pval <- permutationTest(sub$wis.x, sub$wis.y,
                            nPermutation = 999)$pVal.permut
    ##### aggregate by forecast date:
    sub_fcd <- aggregate(cbind(wis.x, wis.y) ~ timezero, data = sub, FUN = mean)
    # catch error if too many observations
    if(nrow(sub_fcd) > 5){
      pval_fcd <- permutationTest(sub_fcd$wis.x, sub_fcd$wis.y,
                                  nPermutation = 999)$pVal.permut
    }else{
      warning("Too few observations to compute p-value for ", mx, " and ", my, " with aggregation by forecast date. Returning NA.")
      pval_fcd <- NA
    }
  }else{
    pval <- NULL
    pval_fcd <- NULL
  }
  return(list(ratio = ratio, pval = pval, pval_fcd = pval_fcd, mx = mx, my = my))
}

# matrices to store:
results_ratio_hzn1 <- matrix(ncol = length(models),
                             nrow = length(models),
                             dimnames = list(models, models))
results_ratio_list <- list(results_ratio_hzn1, results_ratio_hzn1,
                           results_ratio_hzn1, results_ratio_hzn1)

set.seed(123) # set seed for permutation tests

for(mx in seq_along(models)){
  for(my in 1:mx){
    for(hzn in 1:4){
      pwc <- pairwise_comparison(scores = filter(scores, horizon==hzn), 
                                 mx = models[mx], 
                                 my = models[my],
                                 permutation_test = FALSE)
      
      results_ratio_list[[hzn]][mx, my] <- pwc$ratio
      results_ratio_list[[hzn]][my, mx] <- 1/pwc$ratio
    }
  }
}

ind_baseline <- which(rownames(results_ratio_list[[1]]) == "COVIDhub-baseline")
geom_mean_ratios_hzn1 <- exp(rowMeans(log(results_ratio_list[[1]][, -ind_baseline]), na.rm = TRUE))
geom_mean_ratios_hzn2 <- exp(rowMeans(log(results_ratio_list[[2]][, -ind_baseline]), na.rm = TRUE))
geom_mean_ratios_hzn3 <- exp(rowMeans(log(results_ratio_list[[3]][, -ind_baseline]), na.rm = TRUE))
geom_mean_ratios_hzn4 <- exp(rowMeans(log(results_ratio_list[[4]][, -ind_baseline]), na.rm = TRUE))

ratios_baseline_raw_hzn1 <- results_ratio_list[[1]][, "COVIDhub-baseline"] ## avgWIS_model / avgWIS_baseline
ratios_baseline_raw_hzn2 <- results_ratio_list[[2]][, "COVIDhub-baseline"] ## avgWIS_model / avgWIS_baseline
ratios_baseline_raw_hzn3 <- results_ratio_list[[3]][, "COVIDhub-baseline"] ## avgWIS_model / avgWIS_baseline
ratios_baseline_raw_hzn4 <- results_ratio_list[[4]][, "COVIDhub-baseline"] ## avgWIS_model / avgWIS_baseline

ratios_baseline_adj_hzn1 <- geom_mean_ratios_hzn1/geom_mean_ratios_hzn1["COVIDhub-baseline"]
ratios_baseline_adj_hzn2 <- geom_mean_ratios_hzn2/geom_mean_ratios_hzn2["COVIDhub-baseline"]
ratios_baseline_adj_hzn3 <- geom_mean_ratios_hzn3/geom_mean_ratios_hzn3["COVIDhub-baseline"]
ratios_baseline_adj_hzn4 <- geom_mean_ratios_hzn4/geom_mean_ratios_hzn4["COVIDhub-baseline"]

tab <- data.frame(model = c(names(geom_mean_ratios_hzn1), 
                            names(geom_mean_ratios_hzn2),
                            names(geom_mean_ratios_hzn3), 
                            names(geom_mean_ratios_hzn4)),
                  horizon = rep(1:4, each=length(geom_mean_ratios_hzn1)),
                  geom_mean_ratios = c(geom_mean_ratios_hzn1,
                                       geom_mean_ratios_hzn2,
                                       geom_mean_ratios_hzn3,
                                       geom_mean_ratios_hzn4),
                  ratios_baseline_raw = c(ratios_baseline_raw_hzn1,
                                          ratios_baseline_raw_hzn2,
                                          ratios_baseline_raw_hzn3,
                                          ratios_baseline_raw_hzn4),
                  ratios_baseline_adj = c(ratios_baseline_adj_hzn1,
                                          ratios_baseline_adj_hzn2,
                                          ratios_baseline_adj_hzn3,
                                          ratios_baseline_adj_hzn4)
                  )


tab <- tab[order(tab$horizon,tab$ratios_baseline_adj), ]


pairwise_scores <- tab %>%
  mutate(relative_wis = round(ratios_baseline_adj, 2)) %>%
  select(model, horizon, relative_wis)  %>%
  pivot_wider(names_from = "horizon",values_from = "relative_wis")  %>% 
  rename("1 wk relWIS" = "1", "2 wk relWIS" = "2", "3 wk relWIS" = "3", "4 wk relWIS" = "4" ) %>%
  dplyr::rowwise() %>% 
  dplyr::mutate(relative_wis = mean(c_across(where(is.numeric)), na.rm = T)) %>%  
  dplyr::ungroup() %>% 
  arrange(relative_wis)
```


```{r recent relative mae  CASE}

# restrict to 1-4 wk ahead state-level
scores <- inc_scores %>% filter(horizon %in% paste(1:4)) %>%
  filter(score_name %in% c("abs_error", "wis")) %>%
  select("model", "timezero", "location", "horizon", "score_name", "score_value") %>%
  pivot_wider(names_from = score_name, values_from = score_value) %>%
  filter(!is.na(wis)) %>%
  droplevels()

# the included models:
models <- unique(scores$model)

#pairwise comparison function
pairabs_comparison <- function(scores, mx, my, subset = rep(TRUE, nrow(scores)),
                                permutation_test = FALSE){
  # subsets of available scores for both models:
  subx <- subset(scores, model == mx)
  suby <- subset(scores, model == my)
  # merge together and restrict to overlap:
  sub <- merge(subx, suby, by = c("timezero", "location", "horizon"),
               all.x = FALSE, all.y = FALSE)
  ##### catch common problems:
  ##### no overlap between targets covered by x and y:
  if(nrow(sub) == 0){
    warning("No overlap of covered forecast targets for ", mx, "and", my, ". Returning NA.")
    return(list(ratio = NA, pval = NA, pval_fcd = NA, mx = mx, my = my))
  }
  ##### unavailable scores (likely because a model issues only point forecasts?)
  if(any(is.na(subx$abs_error))){
    warning("Some or all wis values are NA for ", mx, ". Returning NA.")
    return(list(ratio = NA, pval = NA, pval_fcd = NA, mx = mx, my = my))
  }
  if(any(is.na(suby$abs_error))){
    warning("Some or all wis values are NA for ", my, ". Returning NA.")
    return(list(ratio = NA, pval = NA, pval_fcd = NA, mx = mx, my = my))
  }

  # compute ratio:

  # matrices to store:
  results_ratio <- results_pval <- results_pval_fcd <- matrix(ncol = length(models),
                                                              nrow = length(models),
                                                              dimnames = list(models, models))

  ratio <- sum(sub$abs_error.x) / sum(sub$abs_error.y)
  # perform permutation tests:
  if(permutation_test){
    pval <- permutationTest(sub$abs_error.x, sub$abs_error.y,
                            nPermutation = 999)$pVal.permut
    ##### aggregate by forecast date:
    sub_fcd <- aggregate(cbind(abs_error.x, abs_error.y) ~ timezero, data = sub, FUN = mean)
    # catch error if too many observations
    if(nrow(sub_fcd) > 5){
      pval_fcd <- permutationTest(sub_fcd$abs_error.x, sub_fcd$abs_error.y,
                                  nPermutation = 999)$pVal.permut
    }else{
      warning("Too few observations to compute p-value for ", mx, " and ", my, " with aggregation by forecast date. Returning NA.")
      pval_fcd <- NA
    }
  }else{
    pval <- NULL
    pval_fcd <- NULL
  }
  return(list(ratio = ratio, pval = pval, pval_fcd = pval_fcd, mx = mx, my = my))
}

# matrices to store:
results_ratio_hzn1 <- matrix(ncol = length(models),
                             nrow = length(models),
                             dimnames = list(models, models))
results_ratio_list <- list(results_ratio_hzn1, results_ratio_hzn1,
                           results_ratio_hzn1, results_ratio_hzn1)

set.seed(123) # set seed for permutation tests

for(mx in seq_along(models)){
  for(my in 1:mx){
    for(hzn in 1:4){
      pwc <- pairabs_comparison(scores = filter(scores, horizon==hzn), 
                                 mx = models[mx], 
                                 my = models[my],
                                 permutation_test = FALSE)
      
      results_ratio_list[[hzn]][mx, my] <- pwc$ratio
      results_ratio_list[[hzn]][my, mx] <- 1/pwc$ratio
    }
  }
}

ind_baseline <- which(rownames(results_ratio_list[[1]]) == "COVIDhub-baseline")
geom_mean_ratios_hzn1 <- exp(rowMeans(log(results_ratio_list[[1]][, -ind_baseline]), na.rm = TRUE))
geom_mean_ratios_hzn2 <- exp(rowMeans(log(results_ratio_list[[2]][, -ind_baseline]), na.rm = TRUE))
geom_mean_ratios_hzn3 <- exp(rowMeans(log(results_ratio_list[[3]][, -ind_baseline]), na.rm = TRUE))
geom_mean_ratios_hzn4 <- exp(rowMeans(log(results_ratio_list[[4]][, -ind_baseline]), na.rm = TRUE))

ratios_baseline_raw_hzn1 <- results_ratio_list[[1]][, "COVIDhub-baseline"] ## avgWIS_model / avgWIS_baseline
ratios_baseline_raw_hzn2 <- results_ratio_list[[2]][, "COVIDhub-baseline"] ## avgWIS_model / avgWIS_baseline
ratios_baseline_raw_hzn3 <- results_ratio_list[[3]][, "COVIDhub-baseline"] ## avgWIS_model / avgWIS_baseline
ratios_baseline_raw_hzn4 <- results_ratio_list[[4]][, "COVIDhub-baseline"] ## avgWIS_model / avgWIS_baseline

ratios_baseline_adj_hzn1 <- geom_mean_ratios_hzn1/geom_mean_ratios_hzn1["COVIDhub-baseline"]
ratios_baseline_adj_hzn2 <- geom_mean_ratios_hzn2/geom_mean_ratios_hzn2["COVIDhub-baseline"]
ratios_baseline_adj_hzn3 <- geom_mean_ratios_hzn3/geom_mean_ratios_hzn3["COVIDhub-baseline"]
ratios_baseline_adj_hzn4 <- geom_mean_ratios_hzn4/geom_mean_ratios_hzn4["COVIDhub-baseline"]

tab <- data.frame(model = c(names(geom_mean_ratios_hzn1), 
                            names(geom_mean_ratios_hzn2),
                            names(geom_mean_ratios_hzn3), 
                            names(geom_mean_ratios_hzn4)),
                  horizon = rep(1:4, each=length(geom_mean_ratios_hzn1)),
                  geom_mean_ratios = c(geom_mean_ratios_hzn1,
                                       geom_mean_ratios_hzn2,
                                       geom_mean_ratios_hzn3,
                                       geom_mean_ratios_hzn4),
                  ratios_baseline_raw = c(ratios_baseline_raw_hzn1,
                                          ratios_baseline_raw_hzn2,
                                          ratios_baseline_raw_hzn3,
                                          ratios_baseline_raw_hzn4),
                  ratios_baseline_adj = c(ratios_baseline_adj_hzn1,
                                          ratios_baseline_adj_hzn2,
                                          ratios_baseline_adj_hzn3,
                                          ratios_baseline_adj_hzn4)
                  )


tab <- tab[order(tab$horizon,tab$ratios_baseline_adj), ]


pairwise_scores_mae <- tab %>%
  mutate(relative_mae = round(ratios_baseline_adj, 2)) %>%
  select(model, horizon, relative_mae)  %>%
  pivot_wider(names_from = "horizon",values_from = "relative_mae")  %>% 

  rename("1 wk relMAE" = "1", "2 wk relMAE" = "2", "3 wk relMAE" = "3", "4 wk relMAE" = "4" ) %>%
  dplyr::rowwise() %>% 
  dplyr::mutate(relative_mae = mean(c_across(where(is.numeric)), na.rm = T)) %>%  
  dplyr::ungroup() %>% 
  arrange(relative_mae)
```

```{r historical relative WIS  CASE}
inc_scores <- case_accuracy_historical %>%
  filter(n_locations >= 25) %>%
  filter(n_weeks >= 4) %>%
  droplevels()

# bring all timezeros to Monday:
inc_scores$timezero <- inc_scores$submission_sat

# restrict to 1-4 wk ahead state-level
scores <- inc_scores %>% filter(horizon %in% paste(1:4),  location %in% US_fips) %>%
  filter(!is.na(score_value)) %>%
  select("model", "timezero", "location", "horizon", "score_name", "score_value") %>%
  filter(score_name %in% c("abs_error", "wis")) %>%
  pivot_wider(names_from = score_name, values_from = score_value) %>% filter(!is.na(wis))

# the included models:
models <- unique(scores$model)



# matrices to store:
results_ratio_hzn1 <- matrix(ncol = length(models),
                             nrow = length(models),
                             dimnames = list(models, models))
results_ratio_list <- list(results_ratio_hzn1, results_ratio_hzn1,
                           results_ratio_hzn1, results_ratio_hzn1)

set.seed(123) # set seed for permutation tests

for(mx in seq_along(models)){
  for(my in 1:mx){
    for(hzn in 1:4){
      pwc <- pairwise_comparison(scores = filter(scores, horizon==hzn), 
                                 mx = models[mx], 
                                 my = models[my],
                                 permutation_test = FALSE)
      
      results_ratio_list[[hzn]][mx, my] <- pwc$ratio
      results_ratio_list[[hzn]][my, mx] <- 1/pwc$ratio
    }
  }
}

ind_baseline <- which(rownames(results_ratio_list[[1]]) == "COVIDhub-baseline")
geom_mean_ratios_hzn1 <- exp(rowMeans(log(results_ratio_list[[1]][, -ind_baseline]), na.rm = TRUE))
geom_mean_ratios_hzn2 <- exp(rowMeans(log(results_ratio_list[[2]][, -ind_baseline]), na.rm = TRUE))
geom_mean_ratios_hzn3 <- exp(rowMeans(log(results_ratio_list[[3]][, -ind_baseline]), na.rm = TRUE))
geom_mean_ratios_hzn4 <- exp(rowMeans(log(results_ratio_list[[4]][, -ind_baseline]), na.rm = TRUE))

ratios_baseline_raw_hzn1 <- results_ratio_list[[1]][, "COVIDhub-baseline"] ## avgWIS_model / avgWIS_baseline
ratios_baseline_raw_hzn2 <- results_ratio_list[[2]][, "COVIDhub-baseline"] ## avgWIS_model / avgWIS_baseline
ratios_baseline_raw_hzn3 <- results_ratio_list[[3]][, "COVIDhub-baseline"] ## avgWIS_model / avgWIS_baseline
ratios_baseline_raw_hzn4 <- results_ratio_list[[4]][, "COVIDhub-baseline"] ## avgWIS_model / avgWIS_baseline

ratios_baseline_adj_hzn1 <- geom_mean_ratios_hzn1/geom_mean_ratios_hzn1["COVIDhub-baseline"]
ratios_baseline_adj_hzn2 <- geom_mean_ratios_hzn2/geom_mean_ratios_hzn2["COVIDhub-baseline"]
ratios_baseline_adj_hzn3 <- geom_mean_ratios_hzn3/geom_mean_ratios_hzn3["COVIDhub-baseline"]
ratios_baseline_adj_hzn4 <- geom_mean_ratios_hzn4/geom_mean_ratios_hzn4["COVIDhub-baseline"]

tab <- data.frame(model = c(names(geom_mean_ratios_hzn1), 
                            names(geom_mean_ratios_hzn2),
                            names(geom_mean_ratios_hzn3), 
                            names(geom_mean_ratios_hzn4)),
                  horizon = rep(1:4, each=length(geom_mean_ratios_hzn1)),
                  geom_mean_ratios = c(geom_mean_ratios_hzn1,
                                       geom_mean_ratios_hzn2,
                                       geom_mean_ratios_hzn3,
                                       geom_mean_ratios_hzn4),
                  ratios_baseline_raw = c(ratios_baseline_raw_hzn1,
                                          ratios_baseline_raw_hzn2,
                                          ratios_baseline_raw_hzn3,
                                          ratios_baseline_raw_hzn4),
                  ratios_baseline_adj = c(ratios_baseline_adj_hzn1,
                                          ratios_baseline_adj_hzn2,
                                          ratios_baseline_adj_hzn3,
                                          ratios_baseline_adj_hzn4)
                  )


tab <- tab[order(tab$horizon,tab$ratios_baseline_adj), ]


historical_wis <- tab %>%
  mutate(relative_wis_historical  = round(ratios_baseline_adj, 2)) %>%
  select(model, horizon, relative_wis_historical) %>% 
  pivot_wider(names_from = "horizon",values_from = "relative_wis_historical")  %>% 
  rename("1 wk relWIS" = "1", "2 wk relWIS" = "2", "3 wk relWIS" = "3", "4 wk relWIS" = "4" )  %>%
    dplyr::rowwise() %>% 
  dplyr::mutate(relative_wis = mean(c_across(where(is.numeric)), na.rm = T)) %>%  
  dplyr::ungroup() %>% 
  arrange(relative_wis)
```

```{r historical relative MAE CASE}
# restrict to 1-4 wk ahead state-level
scores <- inc_scores %>% filter(horizon %in% paste(1:4)) %>%
  filter(score_name %in% c("abs_error", "wis")) %>%
  select("model", "timezero", "location", "horizon", "score_name", "score_value") %>%
  pivot_wider(names_from = score_name, values_from = score_value) %>%
  filter(!is.na(wis)) %>%
  droplevels()

# the included models:
models <- unique(scores$model)

#pairwise comparison function
pairabs_comparison <- function(scores, mx, my, subset = rep(TRUE, nrow(scores)),
                                permutation_test = FALSE){
  # subsets of available scores for both models:
  subx <- subset(scores, model == mx)
  suby <- subset(scores, model == my)
  # merge together and restrict to overlap:
  sub <- merge(subx, suby, by = c("timezero", "location", "horizon"),
               all.x = FALSE, all.y = FALSE)
  ##### catch common problems:
  ##### no overlap between targets covered by x and y:
  if(nrow(sub) == 0){
    warning("No overlap of covered forecast targets for ", mx, "and", my, ". Returning NA.")
    return(list(ratio = NA, pval = NA, pval_fcd = NA, mx = mx, my = my))
  }
  ##### unavailable scores (likely because a model issues only point forecasts?)
  if(any(is.na(subx$abs_error))){
    warning("Some or all wis values are NA for ", mx, ". Returning NA.")
    return(list(ratio = NA, pval = NA, pval_fcd = NA, mx = mx, my = my))
  }
  if(any(is.na(suby$abs_error))){
    warning("Some or all wis values are NA for ", my, ". Returning NA.")
    return(list(ratio = NA, pval = NA, pval_fcd = NA, mx = mx, my = my))
  }

  # compute ratio:

  # matrices to store:
  results_ratio <- results_pval <- results_pval_fcd <- matrix(ncol = length(models),
                                                              nrow = length(models),
                                                              dimnames = list(models, models))

  ratio <- sum(sub$abs_error.x) / sum(sub$abs_error.y)
  # perform permutation tests:
  if(permutation_test){
    pval <- permutationTest(sub$abs_error.x, sub$abs_error.y,
                            nPermutation = 999)$pVal.permut
    ##### aggregate by forecast date:
    sub_fcd <- aggregate(cbind(abs_error.x, abs_error.y) ~ timezero, data = sub, FUN = mean)
    # catch error if too many observations
    if(nrow(sub_fcd) > 5){
      pval_fcd <- permutationTest(sub_fcd$abs_error.x, sub_fcd$abs_error.y,
                                  nPermutation = 999)$pVal.permut
    }else{
      warning("Too few observations to compute p-value for ", mx, " and ", my, " with aggregation by forecast date. Returning NA.")
      pval_fcd <- NA
    }
  }else{
    pval <- NULL
    pval_fcd <- NULL
  }
  return(list(ratio = ratio, pval = pval, pval_fcd = pval_fcd, mx = mx, my = my))
}

# matrices to store:
results_ratio_hzn1 <- matrix(ncol = length(models),
                             nrow = length(models),
                             dimnames = list(models, models))
results_ratio_list <- list(results_ratio_hzn1, results_ratio_hzn1,
                           results_ratio_hzn1, results_ratio_hzn1)

set.seed(123) # set seed for permutation tests

for(mx in seq_along(models)){
  for(my in 1:mx){
    for(hzn in 1:4){
      pwc <- pairabs_comparison(scores = filter(scores, horizon==hzn), 
                                 mx = models[mx], 
                                 my = models[my],
                                 permutation_test = FALSE)
      
      results_ratio_list[[hzn]][mx, my] <- pwc$ratio
      results_ratio_list[[hzn]][my, mx] <- 1/pwc$ratio
    }
  }
}

ind_baseline <- which(rownames(results_ratio_list[[1]]) == "COVIDhub-baseline")
geom_mean_ratios_hzn1 <- exp(rowMeans(log(results_ratio_list[[1]][, -ind_baseline]), na.rm = TRUE))
geom_mean_ratios_hzn2 <- exp(rowMeans(log(results_ratio_list[[2]][, -ind_baseline]), na.rm = TRUE))
geom_mean_ratios_hzn3 <- exp(rowMeans(log(results_ratio_list[[3]][, -ind_baseline]), na.rm = TRUE))
geom_mean_ratios_hzn4 <- exp(rowMeans(log(results_ratio_list[[4]][, -ind_baseline]), na.rm = TRUE))

ratios_baseline_raw_hzn1 <- results_ratio_list[[1]][, "COVIDhub-baseline"] ## avgWIS_model / avgWIS_baseline
ratios_baseline_raw_hzn2 <- results_ratio_list[[2]][, "COVIDhub-baseline"] ## avgWIS_model / avgWIS_baseline
ratios_baseline_raw_hzn3 <- results_ratio_list[[3]][, "COVIDhub-baseline"] ## avgWIS_model / avgWIS_baseline
ratios_baseline_raw_hzn4 <- results_ratio_list[[4]][, "COVIDhub-baseline"] ## avgWIS_model / avgWIS_baseline

ratios_baseline_adj_hzn1 <- geom_mean_ratios_hzn1/geom_mean_ratios_hzn1["COVIDhub-baseline"]
ratios_baseline_adj_hzn2 <- geom_mean_ratios_hzn2/geom_mean_ratios_hzn2["COVIDhub-baseline"]
ratios_baseline_adj_hzn3 <- geom_mean_ratios_hzn3/geom_mean_ratios_hzn3["COVIDhub-baseline"]
ratios_baseline_adj_hzn4 <- geom_mean_ratios_hzn4/geom_mean_ratios_hzn4["COVIDhub-baseline"]

tab <- data.frame(model = c(names(geom_mean_ratios_hzn1), 
                            names(geom_mean_ratios_hzn2),
                            names(geom_mean_ratios_hzn3), 
                            names(geom_mean_ratios_hzn4)),
                  horizon = rep(1:4, each=length(geom_mean_ratios_hzn1)),
                  geom_mean_ratios = c(geom_mean_ratios_hzn1,
                                       geom_mean_ratios_hzn2,
                                       geom_mean_ratios_hzn3,
                                       geom_mean_ratios_hzn4),
                  ratios_baseline_raw = c(ratios_baseline_raw_hzn1,
                                          ratios_baseline_raw_hzn2,
                                          ratios_baseline_raw_hzn3,
                                          ratios_baseline_raw_hzn4),
                  ratios_baseline_adj = c(ratios_baseline_adj_hzn1,
                                          ratios_baseline_adj_hzn2,
                                          ratios_baseline_adj_hzn3,
                                          ratios_baseline_adj_hzn4)
                  )


tab <- tab[order(tab$horizon,tab$ratios_baseline_adj), ]


historical_mae <- tab %>%
  mutate(relative_mae = round(ratios_baseline_adj, 2)) %>%
  select(model, horizon, relative_mae)  %>%
  pivot_wider(names_from = "horizon",values_from = "relative_mae")  %>% 
  rename("1 wk relMAE" = "1", "2 wk relMAE" = "2", "3 wk relMAE" = "3", "4 wk relMAE" = "4" ) %>%
    dplyr::rowwise() %>% 
  dplyr::mutate(relative_mae = mean(c_across(where(is.numeric)), na.rm = T)) %>%  
  dplyr::ungroup() %>% 
  arrange(relative_mae)
```

```{r counts of forecasts by model and create leaderboards for CASES accuracy}
case_count_fcasts_recent <-  case_accuracy_recent %>% group_by(model,score_name) %>%
    summarise(n_forecasts_wis = sum(score_name == "wis" & !is.na(score_value)),
           n_forecasts_mae = sum(score_name == "abs_error" & !is.na(score_value))) %>% ungroup() %>%
  mutate(n_fcast = ifelse(n_forecasts_wis > 0, n_forecasts_wis, n_forecasts_mae)) %>%
  group_by(model) %>%
  summarise("# recent forecasts" = max(n_fcast))

case_count_fcasts_historical <-  case_accuracy_historical %>% group_by(model,score_name) %>%
    summarise(n_forecasts_wis = sum(score_name == "wis" & !is.na(score_value)),
           n_forecasts_mae = sum(score_name == "abs_error" & !is.na(score_value))) %>% ungroup() %>%
  mutate(n_fcast = ifelse(n_forecasts_wis > 0, n_forecasts_wis, n_forecasts_mae)) %>%
  group_by(model) %>%
  summarise("# historical forecasts" = max(n_fcast)) %>%
 ungroup()
  
leaderboard_table <- case_count_fcasts_recent %>%
  full_join(pairwise_scores) %>%
  full_join(pairwise_scores_mae) %>%
  filter(!is.na(relative_mae) | !is.na(relative_wis)) %>% 
  arrange(relative_wis)


leaderboard_table_historical <- case_count_fcasts_historical %>%
  full_join(historical_wis, by = c("model")) %>%
  full_join(historical_mae, by = c("model")) %>%
  filter(!is.na(relative_mae) | !is.na(relative_wis)) %>% 
  arrange(relative_wis)

render <- JS(
  "function(data, type, row) {",
  "  if(type === 'sort' && data === null) {",
  "    return 999999;",
  "  }",
  "  return data;",
  "}"
)
```

```{r}
case_model_order <- leaderboard_table %>%   arrange(relative_wis) %>% pull(model)
case_model_order_historical <- leaderboard_table_historical %>%   arrange(relative_wis) %>% pull(model)
```

### Recent accuracy 
```{r recent Leaderboard CASES accuracy}

# a custom table container
sketch_recent_accuracy = htmltools::withTags(table(
  class = 'display',
  thead(
    tr(
      th(rowspan = 2, "Model"),
      th(rowspan = 2, "# recent forecasts"),
      th(colspan = 4, "Relative WIS"),
      th(colspan = 4, "Relative MAE")
    ),
    tr(
 lapply((c("1 wk","2 wk","3 wk","4 wk","1 wk","2 wk","3 wk","4 wk")), th)))))

leaderboard_table1<- leaderboard_table %>%
 arrange(relative_wis) %>%    
  select (model, "# recent forecasts",  "1 wk relWIS",  "2 wk relWIS","3 wk relWIS","4 wk relWIS","1 wk relMAE","2 wk relMAE","3 wk relMAE","4 wk relMAE") 

datatable(leaderboard_table1,
            rownames= FALSE, 
              options =  list(pageLength = 5, 
                              # order = case_model_order,
                             autoWidth = TRUE,
                             columnDefs = list(list(width = '100px', targets = "_all", render = render)), 
                             ordering = TRUE),
              # filter = c("top")
          colnames = c("Model", "# recent forecasts",  "1 wk relWIS",  "2 wk relWIS","3 wk relWIS","4 wk relWIS","1 wk relMAE","2 wk relMAE","3 wk relMAE","4 wk relMAE"), container=sketch_recent_accuracy) 
              filter = c("top")

```
To calculate each column in our table, different inclusion criteria were applied. This table only includes forecasts for the last `r n_weeks_eval` weeks, since `r format(first_eval_sat, "%B %d, %Y")`.The models included have submitted  at least 50% of forecasts during this time.  The data are initially ordered based on their relative WIS score aggregated across horizons. 

* The column titled, "# recent forecasts" lists the number of forecasts a team has submitted with a target end date over the most recent `r n_weeks_eval` week period.

* Columns 3 through 6 calculate the adjusted relative WIS over the most recent `r n_weeks_eval` week period by horizon.

* Columns 7 through 10 calculate the adjusted relative MAE over the most recent `r n_weeks_eval` week period by horizon. 

### Historical accuracy 
```{r historical Leaderboard CASES accuracy}

# a custom table container
sketch_historical_accuracy = htmltools::withTags(table(
  class = 'display',
  thead(
    tr(
      th(rowspan = 2, "Model"),
      th(rowspan = 2, "# historical forecasts"),
      th(colspan = 4, "Relative WIS"),
      th(colspan = 4, "Relative MAE")
    ),
    tr(
 lapply((c("1 wk","2 wk","3 wk","4 wk","1 wk","2 wk","3 wk","4 wk")), th)))))

leaderboard_table_historical1<- leaderboard_table_historical %>%
 arrange(relative_wis) %>%    
  select (model, "# historical forecasts",  "1 wk relWIS",  "2 wk relWIS","3 wk relWIS","4 wk relWIS","1 wk relMAE","2 wk relMAE","3 wk relMAE","4 wk relMAE") 

datatable(leaderboard_table_historical1,
            rownames= FALSE, 
              options =  list(pageLength = 5, 
                              # order = case_model_order_historical,
                             autoWidth = TRUE,
                             columnDefs = list(list(width = '100px', targets = "_all", render = render)), 
                             ordering = TRUE),
              # filter = c("top")
          colnames = c("Model", "# historical forecasts",  "1 wk relWIS",  "2 wk relWIS","3 wk relWIS","4 wk relWIS","1 wk relMAE","2 wk relMAE","3 wk relMAE","4 wk relMAE"), container=sketch_historical_accuracy) 
              filter = c("top")
```


To calculate each column in our table, different inclusion criteria were applied. This table only includes forecasts for the last `r n_weeks_history` weeks, since `r format(first_eval_sat_hist, "%B %d, %Y")`. The models included have submitted  at least 50% of forecasts during this time. The data are initially  ordered based on their relative WIS score aggregated across horizons. 

* The column titled, "# historical forecasts" lists the number of forecasts a team has submitted with a target end date over the most recent `r n_weeks_history` week period.

* Columns 3 through 6 calculate the adjusted relative WIS over the most recent `r n_weeks_history` week period by horizon.

* Columns 7 through 10 calculate the adjusted relative MAE over the most recent `r n_weeks_history` week period by horizon. 


```{r inclusion in coverage table recent}
#Filtered to include only models in scoreboard (coverage table) 
#at least 5 weeks overall or at least 2 out of the last 3 weeks 
case_coverage_recent <- recent_coverage_filter(score_case_all)
case_coverage_historical <- historical_coverage_filter(score_case_all)

#number of forecasts by model 
case_countc_fcasts_recent <-  case_coverage_recent %>% group_by(model,score_name) %>%
    summarise(n_forecasts_50 = sum(score_name == "coverage_50" & !is.na(score_value)),
           n_forecasts_95 = sum(score_name == "coverage_95" & !is.na(score_value))) %>% ungroup() %>%
  mutate(n_fcast = ifelse(n_forecasts_50 > 0, n_forecasts_50, n_forecasts_95)) %>%
  group_by(model) %>%
  summarise("# recent forecasts" = max(n_fcast)) 

case_countc_fcasts_historical <-  case_coverage_historical %>% group_by(model,score_name) %>%
    summarise(n_forecasts_50 = sum(score_name == "coverage_50" & !is.na(score_value)),
           n_forecasts_95 = sum(score_name == "coverage_95" & !is.na(score_value))) %>% ungroup() %>%
  mutate(n_fcast = ifelse(n_forecasts_50 > 0, n_forecasts_50, n_forecasts_95)) %>%
  group_by(model) %>%
  summarise("# historical forecasts" = max(n_fcast)) 


  historical_calib_50 <-  score_case_all  %>% 
    filter(n_weeks >= 5 |  n_weeks_3wksPrior >= 2) %>% 
    filter(!is.na(score_value))  %>%
    filter(score_name %in% c("coverage_50")) %>%
    select(model,horizon,score_value,n_weeks)  %>%
    group_by(model,horizon) %>%
    summarise(mean_PI50 = round(sum(score_value, na.rm = TRUE) / n(),2)) %>%  
  ungroup()  %>% 
  pivot_wider(names_from = "horizon",values_from = "mean_PI50")  %>% 
  rename("1 wk 50% coverage" = "1", "2 wk 50% coverage" = "2", "3 wk 50% coverage" = "3", "4 wk 50% coverage" = "4" ) %>% 
  dplyr::rowwise() %>% 
  dplyr::mutate(coverage_50 = mean(c_across(where(is.numeric)), na.rm = T)) %>%  
  dplyr::ungroup()
  
  
  recent_calib_50  <- score_case_all  %>%
    filter(n_weeks >= 5 |  n_weeks_3wksPrior >= 2) %>% 
    filter(!is.na(score_value))  %>%
    filter(score_name %in% c("coverage_50")) %>%
    filter(target_end_date >= first_eval_sat) %>%  droplevels() %>%
    select(model,horizon,score_value)  %>%
    group_by(model,horizon) %>%
    summarise(mean_PI50 = round(sum(score_value, na.rm = TRUE) / n(),2)) %>%  
  ungroup()  %>% 
  pivot_wider(names_from = "horizon",values_from = "mean_PI50")  %>% 
  rename("1 wk 50% coverage" = "1", "2 wk 50% coverage" = "2", "3 wk 50% coverage" = "3", "4 wk 50% coverage" = "4" ) %>% 
  dplyr::rowwise() %>% 
  dplyr::mutate(coverage_50 = mean(c_across(where(is.numeric)), na.rm = T)) %>%  
  dplyr::ungroup() 
 
  historical_calib_95 <-  score_case_all  %>% 
    filter(n_weeks >= 5 |  n_weeks_3wksPrior >= 2) %>% 
    filter(!is.na(score_value))  %>%
    filter(score_name %in% c("coverage_95")) %>%
    select(model,horizon,score_value)  %>%
    group_by(model,horizon) %>%
    summarise(mean_PI95 = round(sum(score_value, na.rm = TRUE) / n(),2)) %>%  
  ungroup()  %>% 
  pivot_wider(names_from = "horizon",values_from = "mean_PI95")  %>% 
  rename("1 wk 95% coverage" = "1", "2 wk 95% coverage" = "2", "3 wk 95% coverage" = "3", "4 wk 95% coverage" = "4" ) %>% 
  dplyr::rowwise() %>% 
  dplyr::mutate(coverage_95 = mean(c_across(where(is.numeric)), na.rm = T)) %>%  
  dplyr::mutate(diff_95 = abs(0.95-coverage_95)) %>% 
  dplyr::ungroup()
  
  
  recent_calib_95  <- score_case_all  %>%
    filter(n_weeks >= 5 |  n_weeks_3wksPrior >= 2) %>% 
    filter(!is.na(score_value))  %>%
    filter(score_name %in% c("coverage_95")) %>%
    filter(target_end_date >= first_eval_sat) %>%  droplevels() %>%
    select(model,horizon,score_value)  %>%
    group_by(model,horizon) %>%
    summarise(mean_PI95 = round(sum(score_value, na.rm = TRUE) / n(),2)) %>%  
  ungroup()  %>% 
  pivot_wider(names_from = "horizon",values_from = "mean_PI95")  %>% 
  rename("1 wk 95% coverage" = "1", "2 wk 95% coverage" = "2", "3 wk 95% coverage" = "3", "4 wk 95% coverage" = "4" ) %>% 
  dplyr::rowwise() %>% 
  dplyr::mutate(coverage_95 = mean(c_across(where(is.numeric)), na.rm = T)) %>%  
  dplyr::mutate(diff_95 = abs(0.95-coverage_95)) %>% 
  dplyr::ungroup()
  
  calibration_table  <- case_countc_fcasts_recent %>%
  full_join(recent_calib_50) %>%
  full_join(recent_calib_95) %>%
  filter(!is.na(coverage_95) | !is.na(coverage_50)) %>% 
  arrange(diff_95)
  
  calibration_table_hist  <- case_countc_fcasts_historical %>%
  full_join(historical_calib_50) %>%
  full_join(historical_calib_95) %>%
  filter(!is.na("# historical forecasts"))  %>%
  filter(!is.na("1 wk 50% coverage") | !is.na("1 wk 95% coverage")) %>%
  filter(!is.na(coverage_95) | !is.na(coverage_50)) %>% 
  arrange(diff_95)
  
render <- JS(
  "function(data, type, row) {",
  "  if(type === 'sort' && data === null) {",
  "    return 999999;",
  "  }",
  "  return data;",
  "}"
)
```  
```{r}
calib_model_order <- calibration_table %>%   arrange(diff_95) %>% pull(model)
calib_model_order_historical <- calibration_table_hist %>%   arrange(diff_95) %>% pull(model)
```
 

### Recent coverage

This table only includes forecasts for the last `r n_weeks_eval` weeks, since `r format(first_eval_sat, "%B %d, %Y")`. For inclusion in this table,  a model must have contributed forecasts for 5 or more weeks total during this period, or have submitted forecasts during at least 2 out of the last 3 evaluated weeks. This inclusion criteria was applied in order to score models that submitted for a substantial amount of weeks at any point during the pandemic but may no longer be submitting, while also evaluating new teams that have recently joined our forecasting efforts. The data are initially ordered based on their 95% PI coverage, aggregated across horizons. 

```{r recent Leaderboard CASES coverage}

# a custom table container
sketch_recent_coverage = htmltools::withTags(table(
  class = 'display',
  thead(
    tr(
      th(rowspan = 2, "Model"),
      th(rowspan = 2, "# recent forecasts"),
      th(colspan = 4, "50% PI coverage"),
      th(colspan = 4, "95% PI coverage")
    ),
    tr(
 lapply((c("1 wk","2 wk","3 wk","4 wk","1 wk","2 wk","3 wk","4 wk")), th)))))

calibration_table1<- calibration_table %>%
 arrange(diff_95)%>%    
  select (model, "# recent forecasts",  "1 wk 50% coverage", "2 wk 50% coverage", "3 wk 50% coverage", "4 wk 50% coverage","1 wk 95% coverage", "2 wk 95% coverage", "3 wk 95% coverage", "4 wk 95% coverage") 

datatable(calibration_table1,
            rownames= FALSE, 
              options =  list(pageLength = 5, 
                              # order = list(list(2, 'asc')),
                             autoWidth = TRUE,
                             columnDefs = list(list(width = '100px', targets = "_all", render = render)), 
                             ordering = TRUE),
              # filter = c("top")
          colnames = c("Model", "# recent forecasts",  "1 wk 50% coverage", "2 wk 50% coverage", "3 wk 50% coverage", "4 wk 50% coverage","1 wk 95% coverage", "2 wk 95% coverage", "3 wk 95% coverage", "4 wk 95% coverage"), container=sketch_recent_coverage) 
```


### Historical coverage

This table only includes forecasts for the last `r n_weeks_history` weeks, since `r format(first_eval_sat_hist, "%B %d, %Y")`. For inclusion in this table, a model most have contributed forecasts for 5 or more weeks total during this period, or have submitted forecasts during at least 2 out of the last 3 evaluated weeks. This inclusion criteria was applied in order to score models that submitted for a substantial amount of weeks at any point during the pandemic but may no longer be submitting, while also evaluating new teams that have recently joined our forecasting efforts. The data are initially ordered based on their 95% PI coverage, aggregated across horizons. 

```{r historical Leaderboard CASES coverage}
# a custom table container
sketch_historical_coverage = htmltools::withTags(table(
  class = 'display',
  thead(
    tr(
      th(rowspan = 2, "Model"),
      th(rowspan = 2, "# historical forecasts"),
      th(colspan = 4, "50% PI coverage"),
      th(colspan = 4, "95% PI coverage")
    ),
    tr(
 lapply((c("1 wk","2 wk","3 wk","4 wk","1 wk","2 wk","3 wk","4 wk")), th)))))

calibration_table_hist1<- calibration_table_hist %>%
 arrange(diff_95) %>%    
  select (model, "# historical forecasts",  "1 wk 50% coverage", "2 wk 50% coverage", "3 wk 50% coverage", "4 wk 50% coverage","1 wk 95% coverage", "2 wk 95% coverage", "3 wk 95% coverage", "4 wk 95% coverage") 

datatable(calibration_table_hist1,
            rownames= FALSE, 
              options =  list(pageLength = 5, 
                              # order = list(list(2, 'asc')),
                             autoWidth = TRUE,
                             columnDefs = list(list(width = '100px', targets = "_all", render = render)), 
                             ordering = TRUE),
              # filter = c("top")
          colnames = c("Model", "# recent forecasts",  "1 wk 50% coverage", "2 wk 50% coverage", "3 wk 50% coverage", "4 wk 50% coverage","1 wk 95% coverage", "2 wk 95% coverage", "3 wk 95% coverage", "4 wk 95% coverage"), container=sketch_recent_coverage) 

```  



## WIS components


The data in this graph has been aggregated over all locations and submission weeks. We only included forecasts for the last 10 weeks. The models included have submitted  at least 50% of forecasts during this time. This is the same exclusion criteria applied for WIS scores in the recent evaluation period. 

The sum of the bars adds up to the WIS score. Of note, these values may not be exactly the same as the relative WIS scores shown in the leaderboard table because these are not adjusted for weeks or locations missing.  The data are ordered on the x axis based on their relative WIS score shown in the accuracy table, aggregated across horizons. 

```{r wis bar function, fig.height= 8, fig.width=13}
wis_barplot_function(x = score_case_all, y = pairwise_scores, order = case_model_order)
```


## Evaluation by Week  {.tabset .tabset-fade}

In the following figures, we have evaluated models across multiple forecasting weeks. Points included in this comparison are for models that have submitted probabilistic forecasts for all 50 states. 

For the first 2 figures, WIS is used as a metric. The first figure shows the mean WIS across all 50 states for submission weeks beginning `r format(first_eval_sat_hist, "%B %d, %Y")` at a 1 week horizon. The second figure shows the mean WIS aggregated across locations, however it is for a 4 week horizon.

**To view a specific team, double click on the team names in the legend. To view a value on the plot, click on the point in the forecast of interest. To view a specific time of interest, highlight that section on the graph or use the zoom functionality. **

### 1 Week Horizon WIS
```{r,fig.width=10, fig.height=6}
byweek_case <- by_week_function(score_case_all, var = "wis")
# find 97.5 percentile
b<-byweek_case %>%
  filter(horizon == "4") 
p975<-quantile(b$mean_score,probs=.975, na.rm = TRUE)

by_week_wis_1wk <- plot_byweek_function(byweek_case, var = "WIS", horizon_num = "1") + coord_cartesian(ylim=c(0, p975))
ggplotly(by_week_wis_1wk, tooltip = c("label", "labelx", "labely"))
```

### 4 Week Horizon WIS

In this figure, the dotted black line represents the average 1 week ahead error across all models. There is often larger error for the 4 week horizon compared to the 1 week horizon. 

```{r,fig.width=10, fig.height=6}
#calc 1 week error
meanwis_1wk <- byweek_case %>%
  filter(horizon == "1") %>%
  group_by(target_end_date) %>%
  summarise(mean_score = mean(mean_score, na.rm = TRUE)) %>%
  mutate(model = "`average error for 1 week horizon`",
         horizon = "4") %>%
  select(model, horizon, target_end_date, mean_score)
  

by_week_wis_4wk <- plot_byweek_function(byweek_case, var = "WIS", horizon_num = "4") +
   geom_line(data = meanwis_1wk, aes(label = model, x = target_end_date, y = mean_score), alpha=.5, color = "black", linetype = 2) +
  geom_point(data = meanwis_1wk, aes(x = target_end_date, y = mean_score), alpha=.5, size = 2, color = "black") + coord_cartesian(ylim=c(0, p975))
ggplotly(by_week_wis_4wk,tooltip = c("label", "labelx", "labely"))
```


### 1 Week Horizon 95% PI Coverage

We would expect a well calibrated model to have a value of 95% in this plot. 

```{r,fig.width=10, fig.height=6}
byweek_case <- by_week_function(score_case_all, var = "coverage_95")
by_week_wis_1wk <- plot_byweek_function(byweek_case, var = "95% PI Coverage", horizon_num = "1") +
  geom_hline(yintercept = .95)
ggplotly(by_week_wis_1wk,tooltip = c("label", "labelx", "labely"))
```

### 4 Week Horizon 95% PI Coverage

We would expect a well calibrated model to have a value of 95% in this plot. There is typically larger error for the 4 week horizon compared to the 1 week horizon. 

```{r,fig.width=10, fig.height=6}
by_week_wis_4wk <- plot_byweek_function(byweek_case, var = "95% PI Coverage", horizon_num = "4") +
  geom_hline(yintercept = .95)

ggplotly(by_week_wis_4wk, tooltip = c("label", "labelx", "labely")) 
```



## Evaluation by location {.tabset .tabset-fade}

This figures below show recent model performance stratified by location. We only included forecasts for the last 10 weeks. Models were included if they had submitted forecasts for all 4 horizons and submitted  at least 50% of forecasts during this time.   Locations are sorted by cumulative case counts.. Locations are sorted by cumulative case counts.

The color scheme shows the WIS score relative to the baseline, across all horizons. The only locations evaluated are 50 states and a national level forecast. The data are ordered on the x axis based on their relative WIS score shown in the accuracy table, aggregated across horizons.  

```{r, fig.width=12, fig.height=16}
plot_by_location_wis(case_accuracy_recent, order = case_model_order, location_order  = location_order_case)
```


## Evaluation Periods  {.tabset .tabset-fade}


This figure shows the number of incident reported COVID-19 cases reported each week in the US. The period between the vertical blue line and the black shows the weeks included in the "recent" model evaluations. The period between the vertical red line and the black shows the weeks included in the "historical" model evaluations.

```{r, fig.width=8, fig.height=5}
truth_US_case <- truth_dat_case_all %>%
  filter(location == "US")

plot_truth(dat = truth_US_case, tar="Cases")
```


# Incident Death Forecasts {.tabset .tabset-fade}


## Summary Tables {.tabset .tabset-fade}

Due to technical issues Ohio has with reporting deaths, the most recent 4 weeks of death data for Ohio will not be included in this evaluation.

The first and second tables evaluate recent/historical forecast models based on their WIS and MAE by horizon.  

The third and fourth tables evaluate recent/historical forecast models based on their prediction interval coverage at the 50% and 95% levels by horizon. 

Scores are aggregated separately for the most recent 10 weeks and for 26 historical weeks. 

<!--The table included below evaluated models based on their prediction interval coverage (50% and 95% coverage), and their adjusted relative weighted interval scores (WIS) and adjusted relative mean absolute error (MAE) for a recent and historical number of weeks. 

* The **prediction interval coverage**  measures  the proportion of times a prediction interval of a certain level covered the true value, to assess the degree to which forecasts accurately characterized uncertainty about future observations. Well calibrated models should have a 50% coverage level of 0.5 and a 95% coverage level of 0.95. 

* The **weighted interval score (WIS)** is a proper score that combines a set of interval scores for probabilistic forecasts that provide quantiles of the predictive forecast distribution. To account for the variation in difficult of forecasting different weeks and locations, a pairwis approach was used to calculated the relative adjusted WIS. The code for this comparison can be found [here](https://github.com/jbracher/pairwise_comparisons). A preprint on this method for calculating the WIS can be found [here](https://arxiv.org/pdf/2005.12881.pdf). Models with an adjusted relative WIS  lower than 1 are more accurate than the baseline, and models with an adjusted relative WIS greater than 1 are less accurate than the baseline is predicting the number of incident cases. 

* The **mean absolute error (MAE)** is defined as the the difference between the forecasted value and the actual value. For this calculation, point forecasts submitted by teams were used. When point forecasts were not available, the 0.50 quantile was used. Similar to calculating the WIS, a pairwise approach was used to account for variation across locations and weeks. Models with an adjusted relative MAE lower than 1 are more accurate than the baseline, and models with an adjusted relative MAE greater than 1 are less accurate than the baseline is predicting the number of incident cases. 
-->
 
Inclusion criteria for each column are detailed below the table. 


```{r  recent relative wis  DEATHs}
#at least 50% of recent WIS or 50% of recent MAE
inc_accuracy_recent <- recent_accuracy_filter(score_inc_all_ohio)

inc_scores <- inc_accuracy_recent %>%
  filter(!is.na(score_value)) %>%
  filter(n_locations >= 25) %>% 
  filter(n_weeks >= 4) %>%
  droplevels()

# bring all timezeros to Monday:
inc_scores$timezero <- inc_scores$submission_sat

# restrict to 1-4 wk ahead state-level 
scores <- inc_scores %>% filter(horizon %in% paste(1:4), location %in% US_fips) %>%
  filter(score_name %in% c("wis")) %>%
  select("model", "timezero", "location", "horizon", "score_name", "score_value") %>%
  pivot_wider(names_from = score_name, values_from = score_value) %>%
  filter(!is.na(wis)) %>%
  droplevels()


# the included models:
models <- unique(scores$model)


# matrices to store:
results_ratio_hzn1 <- matrix(ncol = length(models),
                             nrow = length(models),
                             dimnames = list(models, models))
results_ratio_list <- list(results_ratio_hzn1, results_ratio_hzn1,
                           results_ratio_hzn1, results_ratio_hzn1)

set.seed(123) # set seed for permutation tests

for(mx in seq_along(models)){
  for(my in 1:mx){
    for(hzn in 1:4){
      pwc <- pairwise_comparison(scores = filter(scores, horizon==hzn), 
                                 mx = models[mx], 
                                 my = models[my],
                                 permutation_test = FALSE)
      
      results_ratio_list[[hzn]][mx, my] <- pwc$ratio
      results_ratio_list[[hzn]][my, mx] <- 1/pwc$ratio
    }
  }
}

ind_baseline <- which(rownames(results_ratio_list[[1]]) == "COVIDhub-baseline")
geom_mean_ratios_hzn1 <- exp(rowMeans(log(results_ratio_list[[1]][, -ind_baseline]), na.rm = TRUE))
geom_mean_ratios_hzn2 <- exp(rowMeans(log(results_ratio_list[[2]][, -ind_baseline]), na.rm = TRUE))
geom_mean_ratios_hzn3 <- exp(rowMeans(log(results_ratio_list[[3]][, -ind_baseline]), na.rm = TRUE))
geom_mean_ratios_hzn4 <- exp(rowMeans(log(results_ratio_list[[4]][, -ind_baseline]), na.rm = TRUE))

ratios_baseline_raw_hzn1 <- results_ratio_list[[1]][, "COVIDhub-baseline"] ## avgWIS_model / avgWIS_baseline
ratios_baseline_raw_hzn2 <- results_ratio_list[[2]][, "COVIDhub-baseline"] ## avgWIS_model / avgWIS_baseline
ratios_baseline_raw_hzn3 <- results_ratio_list[[3]][, "COVIDhub-baseline"] ## avgWIS_model / avgWIS_baseline
ratios_baseline_raw_hzn4 <- results_ratio_list[[4]][, "COVIDhub-baseline"] ## avgWIS_model / avgWIS_baseline

ratios_baseline_adj_hzn1 <- geom_mean_ratios_hzn1/geom_mean_ratios_hzn1["COVIDhub-baseline"]
ratios_baseline_adj_hzn2 <- geom_mean_ratios_hzn2/geom_mean_ratios_hzn2["COVIDhub-baseline"]
ratios_baseline_adj_hzn3 <- geom_mean_ratios_hzn3/geom_mean_ratios_hzn3["COVIDhub-baseline"]
ratios_baseline_adj_hzn4 <- geom_mean_ratios_hzn4/geom_mean_ratios_hzn4["COVIDhub-baseline"]

tab <- data.frame(model = c(names(geom_mean_ratios_hzn1), 
                            names(geom_mean_ratios_hzn2),
                            names(geom_mean_ratios_hzn3), 
                            names(geom_mean_ratios_hzn4)),
                  horizon = rep(1:4, each=length(geom_mean_ratios_hzn1)),
                  geom_mean_ratios = c(geom_mean_ratios_hzn1,
                                       geom_mean_ratios_hzn2,
                                       geom_mean_ratios_hzn3,
                                       geom_mean_ratios_hzn4),
                  ratios_baseline_raw = c(ratios_baseline_raw_hzn1,
                                          ratios_baseline_raw_hzn2,
                                          ratios_baseline_raw_hzn3,
                                          ratios_baseline_raw_hzn4),
                  ratios_baseline_adj = c(ratios_baseline_adj_hzn1,
                                          ratios_baseline_adj_hzn2,
                                          ratios_baseline_adj_hzn3,
                                          ratios_baseline_adj_hzn4)
                  )


tab <- tab[order(tab$horizon,tab$ratios_baseline_adj), ]


pairwise_scores <- tab %>%
  mutate(relative_wis = round(ratios_baseline_adj, 2)) %>%
  select(model, horizon, relative_wis)  %>%
  pivot_wider(names_from = "horizon",values_from = "relative_wis")  %>% 
  rename("1 wk relWIS" = "1", "2 wk relWIS" = "2", "3 wk relWIS" = "3", "4 wk relWIS" = "4" ) %>%
  dplyr::rowwise() %>% 
  dplyr::mutate(relative_wis = mean(c_across(where(is.numeric)), na.rm = T)) %>%  
  dplyr::ungroup() %>%   
  arrange(relative_wis)
```

```{r recent relative mae  DEATHs}

# restrict to 1-4 wk ahead state-level
scores <- inc_scores %>% filter(horizon %in% paste(1:4)) %>%
  filter(score_name %in% c("abs_error", "wis")) %>%
  select("model", "timezero", "location", "horizon", "score_name", "score_value") %>%
  pivot_wider(names_from = score_name, values_from = score_value) %>%
  filter(!is.na(wis)) %>%
  droplevels()

# the included models:
models <- unique(scores$model)


# matrices to store:
results_ratio_hzn1 <- matrix(ncol = length(models),
                             nrow = length(models),
                             dimnames = list(models, models))
results_ratio_list <- list(results_ratio_hzn1, results_ratio_hzn1,
                           results_ratio_hzn1, results_ratio_hzn1)

set.seed(123) # set seed for permutation tests

for(mx in seq_along(models)){
  for(my in 1:mx){
    for(hzn in 1:4){
      pwc <- pairabs_comparison(scores = filter(scores, horizon==hzn), 
                                 mx = models[mx], 
                                 my = models[my],
                                 permutation_test = FALSE)
      
      results_ratio_list[[hzn]][mx, my] <- pwc$ratio
      results_ratio_list[[hzn]][my, mx] <- 1/pwc$ratio
    }
  }
}

ind_baseline <- which(rownames(results_ratio_list[[1]]) == "COVIDhub-baseline")
geom_mean_ratios_hzn1 <- exp(rowMeans(log(results_ratio_list[[1]][, -ind_baseline]), na.rm = TRUE))
geom_mean_ratios_hzn2 <- exp(rowMeans(log(results_ratio_list[[2]][, -ind_baseline]), na.rm = TRUE))
geom_mean_ratios_hzn3 <- exp(rowMeans(log(results_ratio_list[[3]][, -ind_baseline]), na.rm = TRUE))
geom_mean_ratios_hzn4 <- exp(rowMeans(log(results_ratio_list[[4]][, -ind_baseline]), na.rm = TRUE))

ratios_baseline_raw_hzn1 <- results_ratio_list[[1]][, "COVIDhub-baseline"] ## avgWIS_model / avgWIS_baseline
ratios_baseline_raw_hzn2 <- results_ratio_list[[2]][, "COVIDhub-baseline"] ## avgWIS_model / avgWIS_baseline
ratios_baseline_raw_hzn3 <- results_ratio_list[[3]][, "COVIDhub-baseline"] ## avgWIS_model / avgWIS_baseline
ratios_baseline_raw_hzn4 <- results_ratio_list[[4]][, "COVIDhub-baseline"] ## avgWIS_model / avgWIS_baseline

ratios_baseline_adj_hzn1 <- geom_mean_ratios_hzn1/geom_mean_ratios_hzn1["COVIDhub-baseline"]
ratios_baseline_adj_hzn2 <- geom_mean_ratios_hzn2/geom_mean_ratios_hzn2["COVIDhub-baseline"]
ratios_baseline_adj_hzn3 <- geom_mean_ratios_hzn3/geom_mean_ratios_hzn3["COVIDhub-baseline"]
ratios_baseline_adj_hzn4 <- geom_mean_ratios_hzn4/geom_mean_ratios_hzn4["COVIDhub-baseline"]

tab <- data.frame(model = c(names(geom_mean_ratios_hzn1), 
                            names(geom_mean_ratios_hzn2),
                            names(geom_mean_ratios_hzn3), 
                            names(geom_mean_ratios_hzn4)),
                  horizon = rep(1:4, each=length(geom_mean_ratios_hzn1)),
                  geom_mean_ratios = c(geom_mean_ratios_hzn1,
                                       geom_mean_ratios_hzn2,
                                       geom_mean_ratios_hzn3,
                                       geom_mean_ratios_hzn4),
                  ratios_baseline_raw = c(ratios_baseline_raw_hzn1,
                                          ratios_baseline_raw_hzn2,
                                          ratios_baseline_raw_hzn3,
                                          ratios_baseline_raw_hzn4),
                  ratios_baseline_adj = c(ratios_baseline_adj_hzn1,
                                          ratios_baseline_adj_hzn2,
                                          ratios_baseline_adj_hzn3,
                                          ratios_baseline_adj_hzn4)
                  )


tab <- tab[order(tab$horizon,tab$ratios_baseline_adj), ]


pairwise_scores_mae <- tab %>%
  mutate(relative_mae = round(ratios_baseline_adj, 2)) %>%
  select(model, horizon, relative_mae)  %>%
  pivot_wider(names_from = "horizon",values_from = "relative_mae")  %>% 

  rename("1 wk relMAE" = "1", "2 wk relMAE" = "2", "3 wk relMAE" = "3", "4 wk relMAE" = "4" ) %>%
  dplyr::rowwise() %>% 
  dplyr::mutate(relative_mae = mean(c_across(where(is.numeric)), na.rm = T)) %>%  
  dplyr::ungroup() %>% 
  arrange(relative_mae)
```


```{r historical relative WIS DEATH}
inc_scores <- inc_accuracy_historical %>%
  filter(n_locations >= 25) %>%
  filter(n_weeks >= 4) %>%
  droplevels()

# bring all timezeros to Monday:
inc_scores$timezero <- inc_scores$submission_sat

# restrict to 1-4 wk ahead state-level
scores <- inc_scores %>% filter(horizon %in% paste(1:4),  location %in% US_fips) %>%
  filter(!is.na(score_value)) %>%
  select("model", "timezero", "location", "horizon", "score_name", "score_value") %>%
  filter(score_name %in% c("abs_error", "wis")) %>%
  pivot_wider(names_from = score_name, values_from = score_value) %>% filter(!is.na(wis))

# the included models:
models <- unique(scores$model)



# matrices to store:
results_ratio_hzn1 <- matrix(ncol = length(models),
                             nrow = length(models),
                             dimnames = list(models, models))
results_ratio_list <- list(results_ratio_hzn1, results_ratio_hzn1,
                           results_ratio_hzn1, results_ratio_hzn1)

set.seed(123) # set seed for permutation tests

for(mx in seq_along(models)){
  for(my in 1:mx){
    for(hzn in 1:4){
      pwc <- pairwise_comparison(scores = filter(scores, horizon==hzn), 
                                 mx = models[mx], 
                                 my = models[my],
                                 permutation_test = FALSE)
      
      results_ratio_list[[hzn]][mx, my] <- pwc$ratio
      results_ratio_list[[hzn]][my, mx] <- 1/pwc$ratio
    }
  }
}

ind_baseline <- which(rownames(results_ratio_list[[1]]) == "COVIDhub-baseline")
geom_mean_ratios_hzn1 <- exp(rowMeans(log(results_ratio_list[[1]][, -ind_baseline]), na.rm = TRUE))
geom_mean_ratios_hzn2 <- exp(rowMeans(log(results_ratio_list[[2]][, -ind_baseline]), na.rm = TRUE))
geom_mean_ratios_hzn3 <- exp(rowMeans(log(results_ratio_list[[3]][, -ind_baseline]), na.rm = TRUE))
geom_mean_ratios_hzn4 <- exp(rowMeans(log(results_ratio_list[[4]][, -ind_baseline]), na.rm = TRUE))

ratios_baseline_raw_hzn1 <- results_ratio_list[[1]][, "COVIDhub-baseline"] ## avgWIS_model / avgWIS_baseline
ratios_baseline_raw_hzn2 <- results_ratio_list[[2]][, "COVIDhub-baseline"] ## avgWIS_model / avgWIS_baseline
ratios_baseline_raw_hzn3 <- results_ratio_list[[3]][, "COVIDhub-baseline"] ## avgWIS_model / avgWIS_baseline
ratios_baseline_raw_hzn4 <- results_ratio_list[[4]][, "COVIDhub-baseline"] ## avgWIS_model / avgWIS_baseline

ratios_baseline_adj_hzn1 <- geom_mean_ratios_hzn1/geom_mean_ratios_hzn1["COVIDhub-baseline"]
ratios_baseline_adj_hzn2 <- geom_mean_ratios_hzn2/geom_mean_ratios_hzn2["COVIDhub-baseline"]
ratios_baseline_adj_hzn3 <- geom_mean_ratios_hzn3/geom_mean_ratios_hzn3["COVIDhub-baseline"]
ratios_baseline_adj_hzn4 <- geom_mean_ratios_hzn4/geom_mean_ratios_hzn4["COVIDhub-baseline"]

tab <- data.frame(model = c(names(geom_mean_ratios_hzn1), 
                            names(geom_mean_ratios_hzn2),
                            names(geom_mean_ratios_hzn3), 
                            names(geom_mean_ratios_hzn4)),
                  horizon = rep(1:4, each=length(geom_mean_ratios_hzn1)),
                  geom_mean_ratios = c(geom_mean_ratios_hzn1,
                                       geom_mean_ratios_hzn2,
                                       geom_mean_ratios_hzn3,
                                       geom_mean_ratios_hzn4),
                  ratios_baseline_raw = c(ratios_baseline_raw_hzn1,
                                          ratios_baseline_raw_hzn2,
                                          ratios_baseline_raw_hzn3,
                                          ratios_baseline_raw_hzn4),
                  ratios_baseline_adj = c(ratios_baseline_adj_hzn1,
                                          ratios_baseline_adj_hzn2,
                                          ratios_baseline_adj_hzn3,
                                          ratios_baseline_adj_hzn4)
                  )


tab <- tab[order(tab$horizon,tab$ratios_baseline_adj), ]


historical_wis <- tab %>%
  mutate(relative_wis_historical  = round(ratios_baseline_adj, 2)) %>%
  select(model, horizon, relative_wis_historical) %>% 
  pivot_wider(names_from = "horizon",values_from = "relative_wis_historical")  %>% 
  rename("1 wk relWIS" = "1", "2 wk relWIS" = "2", "3 wk relWIS" = "3", "4 wk relWIS" = "4" )  %>%
    dplyr::rowwise() %>% 
  dplyr::mutate(relative_wis = mean(c_across(where(is.numeric)), na.rm = T)) %>%  
  dplyr::ungroup() %>% 
  arrange(relative_wis)
```

```{r historical relative MAE DEATHS}
# restrict to 1-4 wk ahead state-level
scores <- inc_scores %>% filter(horizon %in% paste(1:4)) %>%
  filter(score_name %in% c("abs_error", "wis")) %>%
  select("model", "timezero", "location", "horizon", "score_name", "score_value") %>%
  pivot_wider(names_from = score_name, values_from = score_value) %>%
  filter(!is.na(wis)) %>%
  droplevels()

# the included models:
models <- unique(scores$model)


# matrices to store:
results_ratio_hzn1 <- matrix(ncol = length(models),
                             nrow = length(models),
                             dimnames = list(models, models))
results_ratio_list <- list(results_ratio_hzn1, results_ratio_hzn1,
                           results_ratio_hzn1, results_ratio_hzn1)

set.seed(123) # set seed for permutation tests

for(mx in seq_along(models)){
  for(my in 1:mx){
    for(hzn in 1:4){
      pwc <- pairabs_comparison(scores = filter(scores, horizon==hzn), 
                                 mx = models[mx], 
                                 my = models[my],
                                 permutation_test = FALSE)
      
      results_ratio_list[[hzn]][mx, my] <- pwc$ratio
      results_ratio_list[[hzn]][my, mx] <- 1/pwc$ratio
    }
  }
}

ind_baseline <- which(rownames(results_ratio_list[[1]]) == "COVIDhub-baseline")
geom_mean_ratios_hzn1 <- exp(rowMeans(log(results_ratio_list[[1]][, -ind_baseline]), na.rm = TRUE))
geom_mean_ratios_hzn2 <- exp(rowMeans(log(results_ratio_list[[2]][, -ind_baseline]), na.rm = TRUE))
geom_mean_ratios_hzn3 <- exp(rowMeans(log(results_ratio_list[[3]][, -ind_baseline]), na.rm = TRUE))
geom_mean_ratios_hzn4 <- exp(rowMeans(log(results_ratio_list[[4]][, -ind_baseline]), na.rm = TRUE))

ratios_baseline_raw_hzn1 <- results_ratio_list[[1]][, "COVIDhub-baseline"] ## avgWIS_model / avgWIS_baseline
ratios_baseline_raw_hzn2 <- results_ratio_list[[2]][, "COVIDhub-baseline"] ## avgWIS_model / avgWIS_baseline
ratios_baseline_raw_hzn3 <- results_ratio_list[[3]][, "COVIDhub-baseline"] ## avgWIS_model / avgWIS_baseline
ratios_baseline_raw_hzn4 <- results_ratio_list[[4]][, "COVIDhub-baseline"] ## avgWIS_model / avgWIS_baseline

ratios_baseline_adj_hzn1 <- geom_mean_ratios_hzn1/geom_mean_ratios_hzn1["COVIDhub-baseline"]
ratios_baseline_adj_hzn2 <- geom_mean_ratios_hzn2/geom_mean_ratios_hzn2["COVIDhub-baseline"]
ratios_baseline_adj_hzn3 <- geom_mean_ratios_hzn3/geom_mean_ratios_hzn3["COVIDhub-baseline"]
ratios_baseline_adj_hzn4 <- geom_mean_ratios_hzn4/geom_mean_ratios_hzn4["COVIDhub-baseline"]

tab <- data.frame(model = c(names(geom_mean_ratios_hzn1), 
                            names(geom_mean_ratios_hzn2),
                            names(geom_mean_ratios_hzn3), 
                            names(geom_mean_ratios_hzn4)),
                  horizon = rep(1:4, each=length(geom_mean_ratios_hzn1)),
                  geom_mean_ratios = c(geom_mean_ratios_hzn1,
                                       geom_mean_ratios_hzn2,
                                       geom_mean_ratios_hzn3,
                                       geom_mean_ratios_hzn4),
                  ratios_baseline_raw = c(ratios_baseline_raw_hzn1,
                                          ratios_baseline_raw_hzn2,
                                          ratios_baseline_raw_hzn3,
                                          ratios_baseline_raw_hzn4),
                  ratios_baseline_adj = c(ratios_baseline_adj_hzn1,
                                          ratios_baseline_adj_hzn2,
                                          ratios_baseline_adj_hzn3,
                                          ratios_baseline_adj_hzn4)
                  )


tab <- tab[order(tab$horizon,tab$ratios_baseline_adj), ]


historical_mae <- tab %>%
  mutate(relative_mae = round(ratios_baseline_adj, 2)) %>%
  select(model, horizon, relative_mae)  %>%
  pivot_wider(names_from = "horizon",values_from = "relative_mae")  %>% 
  rename("1 wk relMAE" = "1", "2 wk relMAE" = "2", "3 wk relMAE" = "3", "4 wk relMAE" = "4" ) %>%
    dplyr::rowwise() %>% 
  dplyr::mutate(relative_mae = mean(c_across(where(is.numeric)), na.rm = T)) %>%  
  dplyr::ungroup() %>% 
  arrange(relative_mae)
```



```{r counts of forecasts by model and create leaderboards for DEATHS accuracy}
inc_count_fcasts_recent <-  inc_accuracy_recent %>% group_by(model,score_name) %>%
    summarise(n_forecasts_wis = sum(score_name == "wis" & !is.na(score_value)),
           n_forecasts_mae = sum(score_name == "abs_error" & !is.na(score_value))) %>% ungroup() %>%
  mutate(n_fcast = ifelse(n_forecasts_wis > 0, n_forecasts_wis, n_forecasts_mae)) %>%
  group_by(model) %>%
  summarise("# recent forecasts" = max(n_fcast))

inc_count_fcasts_historical <-  inc_accuracy_historical %>% group_by(model,score_name) %>%
    summarise(n_forecasts_wis = sum(score_name == "wis" & !is.na(score_value)),
           n_forecasts_mae = sum(score_name == "abs_error" & !is.na(score_value))) %>% ungroup() %>%
  mutate(n_fcast = ifelse(n_forecasts_wis > 0, n_forecasts_wis, n_forecasts_mae)) %>%
  group_by(model) %>%
  summarise("# historical forecasts" = max(n_fcast)) %>%
 ungroup()
  
leaderboard_table <- inc_count_fcasts_recent %>%
  full_join(pairwise_scores) %>%
  full_join(pairwise_scores_mae) %>%
  filter(!is.na(relative_mae) | !is.na(relative_wis)) %>% 
  arrange(relative_wis)


leaderboard_table_historical <- inc_count_fcasts_historical %>%
  full_join(historical_wis, by = c("model")) %>%
  full_join(historical_mae, by = c("model")) %>%
  filter(!is.na(relative_mae) | !is.na(relative_wis)) %>% 
  arrange(relative_wis)

render <- JS(
  "function(data, type, row) {",
  "  if(type === 'sort' && data === null) {",
  "    return 999999;",
  "  }",
  "  return data;",
  "}"
)
```


```{r}
inc_model_order <- leaderboard_table %>%   arrange(relative_wis) %>% pull(model)
inc_model_order_historical <- leaderboard_table_historical %>%   arrange(relative_wis) %>% pull(model)
```


### Recent accuracy 
```{r recent Leaderboard DEATHS accuracy}

# a custom table container
sketch_recent_accuracy = htmltools::withTags(table(
  class = 'display',
  thead(
    tr(
      th(rowspan = 2, "Model"),
      th(rowspan = 2, "# recent forecasts"),
      th(colspan = 4, "Relative WIS"),
      th(colspan = 4, "Relative MAE")
    ),
    tr(
 lapply((c("1 wk","2 wk","3 wk","4 wk","1 wk","2 wk","3 wk","4 wk")), th)))))

leaderboard_table1<- leaderboard_table %>%
 arrange(relative_wis) %>%    
  select (model, "# recent forecasts",  "1 wk relWIS",  "2 wk relWIS","3 wk relWIS","4 wk relWIS","1 wk relMAE","2 wk relMAE","3 wk relMAE","4 wk relMAE") 

datatable(leaderboard_table1,
            rownames= FALSE, 
              options =  list(pageLength = 5, 
                              # order = case_model_order,
                             autoWidth = TRUE,
                             columnDefs = list(list(width = '100px', targets = "_all", render = render)), 
                             ordering = TRUE),
              # filter = c("top")
          colnames = c("Model", "# recent forecasts",  "1 wk relWIS",  "2 wk relWIS","3 wk relWIS","4 wk relWIS","1 wk relMAE","2 wk relMAE","3 wk relMAE","4 wk relMAE"), container=sketch_recent_accuracy) 
              filter = c("top")

```

To calculate each column in our table, different inclusion criteria were applied. This table only includes forecasts for the last `r n_weeks_eval` weeks, since `r format(first_eval_sat, "%B %d, %Y")`.The models included have submitted  at least 50% of forecasts during this time.  The data are initially ordered based on their relative WIS score aggregated across horizons. 


* The column titled, "# recent forecasts" lists the number of forecasts a team has submitted with a target end date over the most recent `r n_weeks_eval` week period.

* Columns 3 through 6 calculate the adjusted relative WIS over the most recent `r n_weeks_eval` week period by horizon.

* Columns 7 through 10 calculate the adjusted relative MAE over the most recent `r n_weeks_eval` week period by horizon. 


### Historical accuracy 
```{r historical Leaderboard DEATHS accuracy}

# a custom table container
sketch_historical_accuracy = htmltools::withTags(table(
  class = 'display',
  thead(
    tr(
      th(rowspan = 2, "Model"),
      th(rowspan = 2, "# historical forecasts"),
      th(colspan = 4, "Relative WIS"),
      th(colspan = 4, "Relative MAE")
    ),
    tr(
 lapply((c("1 wk","2 wk","3 wk","4 wk","1 wk","2 wk","3 wk","4 wk")), th)))))

leaderboard_table_historical1<- leaderboard_table_historical %>%
 arrange(relative_wis) %>%    
  select (model, "# historical forecasts",  "1 wk relWIS",  "2 wk relWIS","3 wk relWIS","4 wk relWIS","1 wk relMAE","2 wk relMAE","3 wk relMAE","4 wk relMAE") 

datatable(leaderboard_table_historical1,
            rownames= FALSE, 
              options =  list(pageLength = 5, 
                              # order = case_model_order_historical,
                             autoWidth = TRUE,
                             columnDefs = list(list(width = '100px', targets = "_all", render = render)), 
                             ordering = TRUE),
              # filter = c("top")
          colnames = c("Model", "# historical forecasts",  "1 wk relWIS",  "2 wk relWIS","3 wk relWIS","4 wk relWIS","1 wk relMAE","2 wk relMAE","3 wk relMAE","4 wk relMAE"), container=sketch_historical_accuracy) 
              filter = c("top")
```


To calculate each column in our table, different inclusion criteria were applied. This table only includes forecasts for the last `r n_weeks_history` weeks, since `r format(first_eval_sat_hist, "%B %d, %Y")`. The models included have submitted  at least 50% of forecasts during this time. The data are initially  ordered based on their relative WIS score aggregated across horizons.  

* The column titled, "# historical forecasts" lists the number of forecasts a team has submitted with a target end date over the most recent `r n_weeks_history` week period.

* Columns 3 through 6 calculate the adjusted relative WIS over the most recent `r n_weeks_history` week period by horizon.

* Columns 7 through 10 calculate the adjusted relative MAE over the most recent `r n_weeks_history` week period by horizon. 


For inclusion in this table, a model most have contributed forecasts for 5 or more weeks total since `r format(first_eval_sat_hist, "%B %d, %Y")`, or have submitted forecasts during at least 2 out of the last 3 evaluated weeks. This inclusion criteria was applied in order to score models that submitted for a substantial amount of weeks at any point during the pandemic but may no longer be submitting, while also evaluating new teams that have recently joined our forecasting efforts. 


```{r inclusion in coverage table recent: DEATHS}
#Filtered to include only models in scoreboard (coverage table) 
#at least 5 weeks overall or at least 2 out of the last 3 weeks 
inc_coverage_recent <- recent_coverage_filter(score_inc_all_ohio)
inc_coverage_historical <- historical_coverage_filter(score_inc_all_ohio)

#number of forecasts by model 
inc_countc_fcasts_recent <-  inc_coverage_recent %>% group_by(model,score_name) %>%
    summarise(n_forecasts_50 = sum(score_name == "coverage_50" & !is.na(score_value)),
           n_forecasts_95 = sum(score_name == "coverage_95" & !is.na(score_value))) %>% ungroup() %>%
  mutate(n_fcast = ifelse(n_forecasts_50 > 0, n_forecasts_50, n_forecasts_95)) %>%
  group_by(model) %>%
  summarise("# recent forecasts" = max(n_fcast)) 

inc_countc_fcasts_historical <-  inc_coverage_historical %>% group_by(model,score_name) %>%
    summarise(n_forecasts_50 = sum(score_name == "coverage_50" & !is.na(score_value)),
           n_forecasts_95 = sum(score_name == "coverage_95" & !is.na(score_value))) %>% ungroup() %>%
  mutate(n_fcast = ifelse(n_forecasts_50 > 0, n_forecasts_50, n_forecasts_95)) %>%
  group_by(model) %>%
  summarise("# historical forecasts" = max(n_fcast)) 

  
  historical_calib_50 <-  score_inc_all_ohio  %>% 
    filter(n_weeks >= 5 |  n_weeks_3wksPrior >= 2) %>% 
    filter(!is.na(score_value))  %>%
    filter(score_name %in% c("coverage_50")) %>%
    select(model,horizon,score_value,n_weeks)  %>%
    group_by(model,horizon) %>%
    summarise(mean_PI50 = round(sum(score_value, na.rm = TRUE) / n(),2)) %>%  
  ungroup()  %>% 
  pivot_wider(names_from = "horizon",values_from = "mean_PI50")  %>% 
  rename("1 wk 50% coverage" = "1", "2 wk 50% coverage" = "2", "3 wk 50% coverage" = "3", "4 wk 50% coverage" = "4" ) %>% 
  dplyr::rowwise() %>% 
  dplyr::mutate(coverage_50 = mean(c_across(where(is.numeric)), na.rm = T)) %>%  
  dplyr::ungroup()
  
  
  recent_calib_50  <- score_inc_all_ohio  %>%
    filter(n_weeks >= 5 |  n_weeks_3wksPrior >= 2) %>% 
    filter(!is.na(score_value))  %>%
    filter(score_name %in% c("coverage_50")) %>%
    filter(target_end_date >= first_eval_sat) %>%  droplevels() %>%
    select(model,horizon,score_value)  %>%
    group_by(model,horizon) %>%
    summarise(mean_PI50 = round(sum(score_value, na.rm = TRUE) / n(),2)) %>%  
  ungroup()  %>% 
  pivot_wider(names_from = "horizon",values_from = "mean_PI50")  %>% 
  rename("1 wk 50% coverage" = "1", "2 wk 50% coverage" = "2", "3 wk 50% coverage" = "3", "4 wk 50% coverage" = "4" ) %>% 
  dplyr::rowwise() %>% 
  dplyr::mutate(coverage_50 = mean(c_across(where(is.numeric)), na.rm = T)) %>%  
  dplyr::ungroup() 
 
  historical_calib_95 <- score_inc_all_ohio  %>% 
    filter(n_weeks >= 5 |  n_weeks_3wksPrior >= 2) %>% 
    filter(!is.na(score_value))  %>%
    filter(score_name %in% c("coverage_95")) %>%
    select(model,horizon,score_value)  %>%
    group_by(model,horizon) %>%
    summarise(mean_PI95 = round(sum(score_value, na.rm = TRUE) / n(),2)) %>%  
  ungroup()  %>% 
  pivot_wider(names_from = "horizon",values_from = "mean_PI95")  %>% 
  rename("1 wk 95% coverage" = "1", "2 wk 95% coverage" = "2", "3 wk 95% coverage" = "3", "4 wk 95% coverage" = "4" ) %>% 
  dplyr::rowwise() %>% 
  dplyr::mutate(coverage_95 = mean(c_across(where(is.numeric)), na.rm = T)) %>%  
  dplyr::mutate(diff_95 = abs(0.95-coverage_95)) %>% 
  dplyr::ungroup()
  
  
  recent_calib_95  <- score_inc_all_ohio  %>%
    filter(n_weeks >= 5 |  n_weeks_3wksPrior >= 2) %>% 
    filter(!is.na(score_value))  %>%
    filter(score_name %in% c("coverage_95")) %>%
    filter(target_end_date >= first_eval_sat) %>%  droplevels() %>%
    select(model,horizon,score_value)  %>%
    group_by(model,horizon) %>%
    summarise(mean_PI95 = round(sum(score_value, na.rm = TRUE) / n(),2)) %>%  
  ungroup()  %>% 
  pivot_wider(names_from = "horizon",values_from = "mean_PI95")  %>% 
  rename("1 wk 95% coverage" = "1", "2 wk 95% coverage" = "2", "3 wk 95% coverage" = "3", "4 wk 95% coverage" = "4" ) %>% 
  dplyr::rowwise() %>% 
  dplyr::mutate(coverage_95 = mean(c_across(where(is.numeric)), na.rm = T)) %>%  
  dplyr::mutate(diff_95 = abs(0.95-coverage_95)) %>% 
  dplyr::ungroup()
  
  calibration_table  <- inc_countc_fcasts_recent %>%
  full_join(recent_calib_50) %>%
  full_join(recent_calib_95) %>%
  filter(!is.na(coverage_95) | !is.na(coverage_50)) %>% 
  arrange(diff_95)
  
  calibration_table_hist  <- inc_countc_fcasts_historical %>%
  full_join(historical_calib_50) %>%
  full_join(historical_calib_95) %>%
  filter(!is.na("# historical forecasts"))  %>%
  filter(!is.na("1 wk 50% coverage") | !is.na("1 wk 95% coverage")) %>%
  filter(!is.na(coverage_95) | !is.na(coverage_50)) %>% 
  arrange(diff_95)
  
render <- JS(
  "function(data, type, row) {",
  "  if(type === 'sort' && data === null) {",
  "    return 999999;",
  "  }",
  "  return data;",
  "}"
)
```

```{r}
calib_model_order <- calibration_table %>%   arrange(diff_95) %>% pull(model)
calib_model_order_historical <- calibration_table_hist %>%   arrange(diff_95) %>% pull(model)
```
 

### Recent coverage

This table only includes forecasts for the last `r n_weeks_eval` weeks, since `r format(first_eval_sat, "%B %d, %Y")`. For inclusion in this table,  a model must have contributed forecasts for 5 or more weeks total during this period, or have submitted forecasts during at least 2 out of the last 3 evaluated weeks. This inclusion criteria was applied in order to score models that submitted for a substantial amount of weeks at any point during the pandemic but may no longer be submitting, while also evaluating new teams that have recently joined our forecasting efforts. The data are initially ordered based on their 95% PI coverage, aggregated across horizons. 

```{r recent Leaderboard DEATHS coverage}

# a custom table container
sketch_recent_coverage = htmltools::withTags(table(
  class = 'display',
  thead(
    tr(
      th(rowspan = 2, "Model"),
      th(rowspan = 2, "# recent forecasts"),
      th(colspan = 4, "50% PI coverage"),
      th(colspan = 4, "95% PI coverage")
    ),
    tr(
 lapply((c("1 wk","2 wk","3 wk","4 wk","1 wk","2 wk","3 wk","4 wk")), th)))))

calibration_table1<- calibration_table %>%
 arrange(diff_95)%>%    
  select (model, "# recent forecasts",  "1 wk 50% coverage", "2 wk 50% coverage", "3 wk 50% coverage", "4 wk 50% coverage","1 wk 95% coverage", "2 wk 95% coverage", "3 wk 95% coverage", "4 wk 95% coverage") 

datatable(calibration_table1,
            rownames= FALSE, 
              options =  list(pageLength = 5, 
                              # order = list(list(2, 'asc')),
                             autoWidth = TRUE,
                             columnDefs = list(list(width = '100px', targets = "_all", render = render)), 
                             ordering = TRUE),
              # filter = c("top")
          colnames = c("Model", "# recent forecasts",  "1 wk 50% coverage", "2 wk 50% coverage", "3 wk 50% coverage", "4 wk 50% coverage","1 wk 95% coverage", "2 wk 95% coverage", "3 wk 95% coverage", "4 wk 95% coverage"), container=sketch_recent_coverage) 
```


### Historical coverage

This table only includes forecasts for the last `r n_weeks_history` weeks, since `r format(first_eval_sat_hist, "%B %d, %Y")`. For inclusion in this table, a model most have contributed forecasts for 5 or more weeks total during this period, or have submitted forecasts during at least 2 out of the last 3 evaluated weeks. This inclusion criteria was applied in order to score models that submitted for a substantial amount of weeks at any point during the pandemic but may no longer be submitting, while also evaluating new teams that have recently joined our forecasting efforts. The data are initially ordered based on their 95% PI coverage, aggregated across horizons. 


```{r historical Leaderboard DEATHS coverage}
# a custom table container
sketch_historical_coverage = htmltools::withTags(table(
  class = 'display',
  thead(
    tr(
      th(rowspan = 2, "Model"),
      th(rowspan = 2, "# historical forecasts"),
      th(colspan = 4, "50% PI coverage"),
      th(colspan = 4, "95% PI coverage")
    ),
    tr(
 lapply((c("1 wk","2 wk","3 wk","4 wk","1 wk","2 wk","3 wk","4 wk")), th)))))

calibration_table_hist1<- calibration_table_hist %>%
 arrange(diff_95) %>%    
  select (model, "# historical forecasts",  "1 wk 50% coverage", "2 wk 50% coverage", "3 wk 50% coverage", "4 wk 50% coverage","1 wk 95% coverage", "2 wk 95% coverage", "3 wk 95% coverage", "4 wk 95% coverage") 

datatable(calibration_table_hist1,
            rownames= FALSE, 
              options =  list(pageLength = 5, 
                              # order = list(list(2, 'asc')),
                             autoWidth = TRUE,
                             columnDefs = list(list(width = '100px', targets = "_all", render = render)), 
                             ordering = TRUE),
              # filter = c("top")
          colnames = c("Model", "# recent forecasts",  "1 wk 50% coverage", "2 wk 50% coverage", "3 wk 50% coverage", "4 wk 50% coverage","1 wk 95% coverage", "2 wk 95% coverage", "3 wk 95% coverage", "4 wk 95% coverage"), container=sketch_recent_coverage) 

```  



## WIS components

The data in this graph has been aggregated over all locations and submission weeks. We only included forecasts for the last 10 weeks. The models included have submitted  at least 50% of forecasts during this time. This is the same exclusion criteria applied for WIS scores in the recent evaluation period. 

The sum of the bars adds up to the WIS score. Of note, these values may not be exactly the same as the relative WIS scores shown in the leaderboard table because these are not adjusted for weeks or locations missing.  The data are ordered on the x axis based on their relative WIS score shown in the accuracy table, aggregated across horizons.  

```{r wis bar function DEATHS, fig.height=8, fig.width=13}
wis_barplot_function(score_inc_all_ohio, y = pairwise_scores, order = inc_model_order)
```


## Evaluation by Week  {.tabset .tabset-fade}

In the following figures, we have evaluated models across multiple forecasting weeks. Points included in this comparison are for models that have submitted probabilistic forecasts for all 50 states. 

For the first 2 figures, WIS is used as a metric. The first figure shows the mean WIS across all 50 states for submission weeks beginning `r format(first_eval_sat_hist, "%B %d, %Y")` at a 1 week horizon. The second figure shows the mean WIS aggregated across locations, however it is for a 4 week horizon.

**To view a specific team, double click on the team names in the legend. To view a value on the plot, click on the point in the forecast of interest.To view a specific time of interest, highlight that section on the graph or use the zoom functionality.**

### 1 Week Horizon WIS
```{r,fig.width=10, fig.height=6}
byweek_inc <- by_week_function(score_inc_all_ohio, var = "wis")
# find 97.5 percentile
b_inc<-byweek_inc %>%
  filter(horizon == "4") 
p975_inc<-quantile(b_inc$mean_score,probs=.975, na.rm = TRUE)
by_week_wis_1wk <- plot_byweek_function(byweek_inc, var = "WIS", horizon_num = "1") +
  geom_hline(yintercept = .95)+ coord_cartesian(ylim=c(0, p975_inc))
ggplotly(by_week_wis_1wk, tooltip = c("label", "labelx", "labely"))
```


### 4 Week Horizon WIS

In this figure, the dotted black line represents the average 1 week ahead error across all models. There is often larger error for the 4 week horizon compared to the 1 week horizon. 

```{r,fig.width=10, fig.height=6}
#calc 1 week error
meanwis_1wk <- byweek_inc %>%
  filter(horizon == "1") %>%
  group_by(target_end_date) %>%
  summarise(mean_score = mean(mean_score, na.rm = TRUE)) %>%
  mutate(model = "`average wis or 1 week horizon`",
         horizon = "4") %>%
  select(model, horizon, target_end_date, mean_score)
  
by_week_wis_4wk <- plot_byweek_function(byweek_inc, var = "wis", horizon_num = "4") +
   geom_line(data = meanwis_1wk, aes(x = target_end_date, y = mean_score), alpha=.5, color = "black", linetype = 2) +
  geom_point(data = meanwis_1wk, aes(x = target_end_date, y = mean_score), alpha=.5, size = 2, color = "black") + coord_cartesian(ylim=c(0, p975_inc))
ggplotly(by_week_wis_4wk,tooltip = c("label", "labelx", "labely"))
```


### 1 Week Horizon 95% PI Coverage

We would expect a well calibrated model to have a value of 95% in this plot. 
```{r,fig.width=10, fig.height=6}
byweek_inc <- by_week_function(score_inc_all_ohio, var = "coverage_95")
by_week_wis_1wk <- plot_byweek_function(byweek_inc, var = "95% PI Coverage", horizon_num = "1") +
  geom_hline(yintercept = .95)
ggplotly(by_week_wis_1wk, tooltip = c("label", "labelx", "labely"))
```

### 4 Week Horizon 95% PI Coverage

We would expect a well calibrated model to have a value of 95% in this plot. There is typically larger error for the 4 week horizon compared to the 1 week horizon. 
```{r,fig.width=10, fig.height=6}
by_week_wis_4wk <- plot_byweek_function(byweek_inc, var = "95% PI Coverage", horizon_num = "4") +
  geom_hline(yintercept = .95)

ggplotly(by_week_wis_4wk, tooltip = c("label", "labelx", "labely"))
```


## Evaluation by location {.tabset .tabset-fade}

This figures below show recent model performance stratified by location. We only included forecasts for the last 10 weeks. Models were included if they had submitted forecasts for all 4 horizons and submitted  at least 50% of forecasts during this time.   Locations are sorted by cumulative case counts.

The color scheme shows the WIS score relative to the baseline, across all horizons. The only locations evaluated are 50 states and a national level forecast. The data are ordered on the x axis based on their relative WIS score shown in the accuracy table, aggregated across horizons.  

<!-- ### Evaluation by WIS -->
```{r, fig.width=12, fig.height=16}
plot_by_location_wis(inc_accuracy_recent, order = inc_model_order, location_order = location_order_death)
```

## Evaluation Periods  {.tabset .tabset-fade}


This plot shows the observed number of incident deaths over time in the US. The period between the vertical blue lines shows the weeks included in the "recent" model evaluations.


```{r, fig.width=8, fig.height=5}
truth_US_inc <- truth_dat_inc_all_ohio %>% filter(location == "US") 

plot_truth(truth_US_inc,tar="deaths")
```
