---
title: "CvM Calculation for COVID-19 Forecasting Models - Demo"
author: "Estee Cramer, Nick Reich, Nutcha Wattanachit"
date: "02/23/2021"
header-includes:
   - \usepackage{tabularx}
   - \usepackage{hyperref}
   - \usepackage{wrapfig}
   - \usepackage{float}
   - \usepackage{colortbl}
   - \usepackage{pdflscape}
   - \usepackage{tabu}
   - \usepackage{xcolor}
output:
  pdf_document:
        latex_engine: xelatex
---

```{r setup, include=FALSE}
library(tidyverse)
# cvm packages to compare results
library(energy)
library(twosamples)
library(cramer)
library(CDFt)
library(knitr)
library(data.table)
library(covidHubUtils)
library(zoltr)
library(purrr)
knitr::opts_chunk$set(comment = FALSE, message=FALSE, fig.show= 'hold', fig.pos="h",
                      table.placement='h')
```

# Model Similarity Demo

## Definitions

## Cramer von-Mises criterion

The Cramer von-Mises criterion is defined as 

$$
\omega^2=\int^\infty_{-\infty}[F_n(x)-F^*(x)]^2dF^*(x),
$$
where $F_{n}(x)$ is an empirical cumulative distribution function and $F^*(x)$ is a theoretical cumulative distribution function for a one-sample case. 

The two-sample formulation of CvM criterion can be written in many forms. The equation below is currently used in the first part of this demo (from `cramer::cramer.test()`).

$$
T=\frac{mn}{(m+n)}\Big(\frac{2}{mn}\sum_{i=1..m,j=1..n}^{m,n}\phi(||X_i-Y_j||^2) - \frac{1}{m^2}\sum_{i=1..m,j=1..m}^{m,n} \phi(||X_i-X_j||^2) - \frac{1}{n^2}\sum_{i=1..n,j=1..n}^{m,n} \phi(||Y_i-Y_j||^2)\Big)\\
$$

with $\phi_{\text{Cramer}}(z)=\sqrt{z}/2$. The formula that `twosample` use is $\sum|F_1(x)-F_2(x)|^p$ with $p=2$. The CvM values differ greatly in scale. 


## Cramer's Distance

Cramer's Distance is defined as 

$$
CD(F,G)=\int^\infty_{-\infty}[F(x)-G(x)]^2dx.
$$
For univariate distributions, the Cramer's distance is exactly twice the energy distance. The current implementatino in this demo uses the function `eqdist.e()` from the `energy` package to calculate the energy distance or statistic and then divide the number by 2 to get Cramer's distance. 

## Setup Process

Since we have sample quantiles from COVID-19 forecasting models, we do not have the whole empirical distributions for the CvM calculation. In the current implementation, we do the following:

- The monotonic spline function to interpolate is used to interpolate points between available sample quantiles from the forecasting models. Now we have samples (with points interpolated between sample quantiles and extrapolated at the tails).
- We can apply the `ecdf()` function to create and plot the ecdfs from these samples. For the calculation of CvM, samples created in the first step are  used. 

## Simpler toy example of known distributions

Due to large discrepancies in what we see above. We want to see how those functions compare in this toy example. We simulated 3 discrete uniform distributions:

$$
f_1\sim\text{U}(1,2)\\
f_2\sim\text{U}(1,3)\\
f_3\sim\text{U}(1,10)
$$

```{r}
source("./distance_func_script.R")
# create toy data
n <- 1000
b <- c(2,3,10)
a <- c(1,1,1)
q <- seq(0, 1, by=0.01)
#  fill in bin probs
toy_forecasts <- data.frame(q=q) %>%
   dplyr::mutate(forecast1=sample_quantile(rdunif(n, b[1] , a[1]),q),
                 forecast2=sample_quantile(rdunif(n, b[2] , a[2]),q),
                 forecast3=sample_quantile(rdunif(n, b[3] , a[3]),q))

tnames <- c("forecast1","forecast2","forecast3")
```

We can see the clear step functions here since the distributions are discrete and and the ranges of values are relatively narrow :

```{r,fig.align="center",message=FALSE,warning=FALSE,fig.cap=""}
# cut the tails (-Inf, Inf) out
plot(ecdf(toy_forecasts$forecast1),verticals=TRUE, do.points=FALSE,xlim=c(0,12), 
     col='blue', main="ECDF Plot")
plot(ecdf(toy_forecasts$forecast2),verticals=TRUE, do.points=FALSE, add=TRUE, col='red')
plot(ecdf(toy_forecasts$forecast3),verticals=TRUE, do.points=FALSE, add=TRUE, col='green')
legend("topleft",tnames,fill=c("blue","red","green"))
```

```{r}
p <- seq(0, 1, by=0.001)
for(i in 1:6){
   assign(paste0("tcvm_vals",i),toy_compare(toy_forecasts,
                                            spline_method="hyman",
                                            p,
                                            est_method=i))}
kable(tcvm_vals1,caption="From cramer package")
kable(tcvm_vals2,caption="From twosamples package")
kable(round(tcvm_vals3,2),caption="From  package")
kable(tcvm_vals4,caption="From http://estatcomp.github.io/henrique/exer_chap8.html")
kable(round(tcvm_vals5,3),caption="cramer's distance using energy distance from energy package divided by 2")
kable(round(tcvm_vals6,3),caption="Approx. cramer's distance based on quantile from Johannes")
```

## Distance metrics of Some COVID-19 Forecasting Models

In this demo, the models are from the week of 02/08/2021. 

```{r}
# create sample data for this demo
sample_frame <- load_latest_forecasts(models = c("CU-select", "UMass-MechBayes", "Covid19Sim-Simulator", 
                                                 "COVIDhub-ensemble", "COVIDhub-baseline"),
                              last_forecast_date = "2021-02-08", 
                              forecast_date_window_size = 6,
                              locations = "US", 
                              types = "quantile", 
                              targets = "1 wk ahead inc death",
                              source = "zoltar")

## make a single target data for demo run
small <- frame_format(sample_frame) %>%
   dplyr::filter(type=="quantile") %>%
   data.frame(.)
names <- colnames(small)[6:ncol(small)]
# interpolate points for these quantiles
point_to_interpolate <- seq(0, 1, by=0.001)
for(i in 1:5){
   assign(paste0("emp",i),
          ecdf(spline(x=small$quantile, 
                      y=small[,names[i]], 
                      method = "hyman",
                      xout=point_to_interpolate)$y))
}
```

Plot from the ecdf created from the samples:

```{r,fig.align="center",message=FALSE,warning=FALSE,fig.cap=""}
plot(emp1,verticals=TRUE, do.points=FALSE, col='blue',xlim=c(5000,30000), main="ECDF Plot")
plot(emp2,verticals=TRUE, do.points=FALSE, add=TRUE, col='red')
plot(emp3,verticals=TRUE, do.points=FALSE, add=TRUE, col='green')
plot(emp4,verticals=TRUE, do.points=FALSE, add=TRUE, col='purple')
plot(emp5,verticals=TRUE, do.points=FALSE, add=TRUE, col='brown')
legend("topleft",names,fill=c("blue","red","green","purple","brown"))
```

Now we can create distance matrices for the models.The CvM criterion and Cramer's distance results are the same. Is it possible the author of the `cramer` package confuse CvM with Cramer's distance just like we did? The authors of the `energy` package made it clear that those are different, so I assume they are aware. On the other hand, the approximated Cramer's distance based on quantile look different from the Cramer's distance we see. It is possible that I interpolated so many points and created a large sample (and sample size matters in the calculation of the the distances based on their formula).

```{r}
cvm_mat <- build_distance_frame(small, 
                           spline_method="hyman",
                           target_list=unique(small$target_variable),
                           point_to_interpolate,
                           distance="CvM")
cramer_mat <- build_distance_frame(small, 
                           spline_method="hyman",
                           target_list=unique(small$target_variable),
                           point_to_interpolate,
                           distance="cramer")
approx_cd_mat <- build_distance_frame(small, 
                           target_list=unique(small$target_variable),
                           distance="approx_cramer")
kable(cvm_mat[[1]])
kable(round(cramer_mat[[1]],3))
kable(round(approx_cd_mat[[1]],3))
```

We can visualize matrices above in heat maps shown below.

```{r}
#transf_mat <-log(cvm_mat[[1]])
distance_heatmap(cvm_mat[[1]])
distance_heatmap(round(cramer_mat[[1]],3))
distance_heatmap(round(approx_cd_mat[[1]],3))
```

<!-- ## Comparison of CvM values from various sources -->


<!-- ```{r} -->
<!-- for(i in 1:4){ -->
<!--    assign(paste0("cvm_vals",i),build_CvM_frame_compare(small, -->
<!--                                        spline_method="hyman", -->
<!--                                        target_list=unique(small$target_variable), -->
<!--                                        point_to_interpolate, -->
<!--                                        est_method=i)) -->
<!-- } -->
<!-- kable(cvm_vals1[[1]],caption="From cramer package") -->
<!-- kable(cvm_vals2[[1]],caption="From twosamples package") -->
<!-- kable(round(cvm_vals3[[1]],2),caption="From  package") -->
<!-- kable(cvm_vals4[[1]],caption="From http://estatcomp.github.io/henrique/exer_chap8.html") -->
<!-- ``` -->